\documentclass[11pt,]{article}
\usepackage[margin=1in]{geometry}
\newcommand*{\authorfont}{\fontfamily{phv}\selectfont}
\usepackage[]{mathpazo}
\usepackage{multicol}
\usepackage{abstract}
\renewcommand{\abstractname}{}    % clear the title
\renewcommand{\absnamepos}{empty} % originally center
\newcommand{\blankline}{\quad\pagebreak[2]}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}} 
\usepackage{longtable,booktabs}
      
\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}

\titleformat*{\subsubsection}{\normalsize\itshape}

\usepackage{titling}
\setlength{\droptitle}{-.15cm}

%\setlength{\parindent}{0pt}
%\setlength{\parskip}{6pt plus 2pt minus 1pt}
%\setlength{\emergencystretch}{3em}  % prevent overfull lines 

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{lastpage}
\renewcommand{\headrulewidth}{0.3pt}
\renewcommand{\footrulewidth}{0.0pt} 
\lhead{}
\chead{}
\rhead{\footnotesize SOCI 301: Contemporary Social Theory -- Fall 2022}
\lfoot{}
\cfoot{\small \thepage /\pageref*{LastPage}}
\rfoot{}

\fancypagestyle{firststyle}
{
\renewcommand{\headrulewidth}{0pt}%
   \fancyhf{}
   \fancyfoot[C]{\small \thepage/\pageref*{LastPage}}
}

%\def\labelitemi{--}
%\usepackage{enumitem}
%\setitemize[0]{leftmargin=25pt}
%\setenumerate[0]{leftmargin=25pt}




\makeatletter
\@ifpackageloaded{hyperref}{}{%
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
}
\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
             pdfkeywords = {},  
            pdftitle={SOCI 301: Contemporary Social Theory},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls


\setcounter{secnumdepth}{0}

\usepackage{longtable}




\usepackage{setspace}

\title{SOCI 301: Contemporary Social Theory}
\date{Fall 2022}


\begin{document}  

		\maketitle
		
	
		\thispagestyle{firststyle}

%	\thispagestyle{empty}
\textbf{\underline{Instructor}}
\begin{multicols}{2}

  \textbf{Dr.~Martín Jacinto}\\
  Email: \href{mailto:mjacinto@csuchico.edu}{\nolinkurl{mjacinto@csuchico.edu}}\\
  Preferred contact: Canvas Messaging\\
  Office Hours: 10:00 a.m. - 12:00 p.m. Wed\\
  Office: TBD\\
  Correspondence policy: Respond within 24-48 hours\\
    \columnbreak
    
  \end{multicols}
	
\noindent \begin{tabular*}{\textwidth}{ @{\extracolsep{\fill}} lr @{\extracolsep{\fill}}}
\textbf{\underline{Class information}}\\
  Classroom: Butte Hall 308\\
  Class Hours: 2:00 p.m. - 3:15 p.m. TuTh\\
    \\
	\end{tabular*}\\


\vspace{2mm}


\hypertarget{indigenous-land-statement}{%
\section{Indigenous Land Statement}\label{indigenous-land-statement}}

\begin{quote}
\begin{quote}
\emph{Please be aware that the land on which our campus resides occupies
the territory of the Mechoopda people. Without them, we would not have
access to this campus or our education.}
\end{quote}
\end{quote}

\hypertarget{course-description}{%
\section{Course Description}\label{course-description}}

We all construct and use social theories in our everyday lives. Theory
is simply a means of understanding and explaining the social world
around us. Social theory allows for seeing patterns, forces, and power
relations, encouraging us to make sense of all kinds of social phenomena
-- ranging from everyday interactions between friends to decades of
violent colonization. In this course, we will read theoretical texts
every week, and then we will spend time understanding how they have been
used to understand specific social phenomena. Theory must be relevant to
real life ``social facts'' for it to survive, and we will work toward
bridging the abstract concepts in our readings with the world around us.
By the end of the class, you will likely find that some theories are
your favorites -- more relevant to your everyday life and your own
sociological interests than others.

The goal of this course is to deepen your understanding of sociological
theories that motivate research and inquiry into our society. In this
class, we explore the diversity of major theoretical orientations in
sociological thought since the 1950s. Throughout the course of the
semester, we will compare core concepts and ideas from these theorists
on topics such as social interaction, identity, domination, freedom and
perhaps most importantly, power.

This course requires you to read a lot of social theory, which will be
abstract and difficult. I assign primary texts, meaning that they were
written by the theorist him/herself. The textbook supplements primary
texts by elaborating important notions and concepts across the multipe
theoretical perspectives we will cover in the course. While we will
contextualize the readings by learning about the theorist's life, it is
important that you learn to read with patience and diligence. I am here
to help, as are your classmates. If you are struggling to understand
course material on your own, that's okay! No sociologist learns theory
on their own. In this class we situate the readings within their
historical and biographical contexts and in conversation with other
readings. Through lectures, multiple readings of the material on your
own, and class discussions, we will -- together -- arrive at a deeper
understanding of our social world and of the history of sociological
thought.

\hypertarget{learning-objectives}{%
\section{Learning Objectives}\label{learning-objectives}}

\hypertarget{course-learning-objectives}{%
\subsection{Course Learning
Objectives}\label{course-learning-objectives}}

\begin{itemize}
\tightlist
\item
  Gain knowledge about some of the primary theoretical perspectives used
  within sociology in the 20th and 21st centuries.
\item
  Understand how these perspectives have been shaped by the social
  context in which they arose.
\item
  Explore how these perspectives have impacted sociological research and
  knowledge.
\item
  Evaluate the strengths and weaknesses of each perspective.
\item
  Apply the perspectives to our real lives and to the world around us.
\end{itemize}

\hypertarget{sociology-program-student-learning-objectives}{%
\subsection{Sociology Program Student Learning
Objectives}\label{sociology-program-student-learning-objectives}}

\begin{itemize}
\tightlist
\item
  Demonstrate critical thinking through verbal and written
  communication.
\item
  Apply, critically interpret, and synthesize sociological theory.
\item
  Display an understanding of and appreciation for cultural diversity.
\item
  Identify processes of social control and how they shape our social
  institutions and lives.
\item
  Recognize the relationship between personal agency, social
  responsibility, and social change (sociological imagination).
\item
  Display knowledge of the impact of social institutions on everyday
  lives.
\end{itemize}

\hypertarget{course-status}{%
\subsection{Course Status}\label{course-status}}

This course is a requirement for the sociology major. It has a
prerequisite of SOCI 300, Classical Social Theory, though this
prerequisite may be waived with permission of the instructor. \emph{Note
that if you take SOCI 301 prior to or concurrent with SOCI 300, you will
not be able to repeat SOCI 300 for forgiveness.}

\hypertarget{important-dates}{%
\subsection{Important Dates}\label{important-dates}}

\begin{itemize}
\tightlist
\item
  Sept.~2nd - Last day to drop without instructor's approval\\
\item
  Oct.~24th - Last day to drop and receive financial credit for refund\\
\item
  Nov.~10th - Last day to drop or withdraw\\
\item
  See the
  \href{https://www.csuchico.edu/apss/calendar/aca-cal-2022-23.shtml}{2022-2023
  Academic Calendar} for more information.
\end{itemize}

\hypertarget{course-readings}{%
\section{Course Readings}\label{course-readings}}

\hypertarget{required-textbooks}{%
\subsection{Required Textbooks}\label{required-textbooks}}

\begin{itemize}
\item
  Dillon M (2020). \emph{Introduction to Sociological Theory: Theorists,
  Concepts, and their Applicabilityto the Twenty-First Century}, 3
  edition. Wiley-Blackwell, Hoboken, NJ. ISBN 978-1-119-41091-1.
\item
  We will be using the 3rd edition which looks
  \href{https://www.abebooks.com/Introduction-Sociological-Theory-Theorists-Concepts-Applicability/31208296728/bd?cm_mmc=ggl-_-US_Shopp_Textbook-_-product_id=COM9781119410911USED-_-keyword=\&gclid=Cj0KCQjwuO6WBhDLARIsAIdeyDLJvr2N_LKW1qd-49HuMemlLuCRQT4yR3PKWnmeqMDWBDwy9LNFFRUaAlcyEALw_wcB}{this}.
  Previous editions are not permitted.
\end{itemize}

\hypertarget{additional-required-readings}{%
\subsection{Additional Required
Readings}\label{additional-required-readings}}

\begin{itemize}
\tightlist
\item
  Primary texts and other required readings will be available
  electronically on the Canvas course page and on Perusall. An
  \colorbox{Goldenrod}{\bf{“E-Posting”}} notation is made next to each
  of these readings in the syllabus. These readings will only be
  available to students enrolled in the course, and are to be used only
  for educational purposes.
\end{itemize}

\hypertarget{structure-and-character-of-a-chicoflex-course}{%
\section{Structure and Character of a ChicoFlex
Course}\label{structure-and-character-of-a-chicoflex-course}}

\begin{itemize}
\item
  \textbf{Since this is a
  \href{https://www.csuchico.edu/tlp/chicoflex/faq.shtml\#whatiscoflex}{\emph{ChicoFlex}
  Course}, ALL communications for this course will be conducted via
  Canvas Learn}. At Chico State, ``this class meets at set days/times
  in-person (requiring social distancing and face coverings) and is
  paired with another section taught simultaneously online by the same
  instructor.'' \textbf{All times will use Pacific Standard Time (PST).}
  This means that this class includes campus students who come to a
  physical class, online students who show up ``live,'' and online
  students who watch the archived lectures. Therefore, it is the
  student's responsibility to check Canvas Learn regularly and to check
  in with the professor or review the Syllabus re: any administrative
  questions. \emph{Students are required to email the instructor from
  Canvas Learn (this will ensure instructor access to emails).}
\item
  Also, given the fact that we're still in a global pandemic, the course
  will proceed fluidly. I want this class to work for all of us and will
  remain sensitive to the ongoing needs of students while adhering to
  public health standards and guidelines.
\end{itemize}

\hypertarget{technological-problems}{%
\subsection{Technological Problems:}\label{technological-problems}}

\begin{itemize}
\tightlist
\item
  Occasional problems with technology are a common part of the modern
  university experience. If you have any technical difficulties, you
  \href{https://www.csuchico.edu/itss/}{\textbf{should call IT Support
  Services (ITSS) at 530-898-6000}}. After you call them, if they are
  not able to resolve the issue, please email me with a description of
  the problem, the name of the person you spoke to in that office, what
  they and/or you are doing to resolve the problem, and the expected
  timeline for its resolution. If you are having trouble with Canvas
  Learn during a quiz or other assignment, take a screen shot or photo
  of the computer screen and the error message you receive and email it
  to me AND contact ITSS at 530-898-6000. If you experience technical
  difficulties while submitting an assignment, call ITSS at
  1-800-898-6000 and send a copy of the assignment to me via Canvas
  Learn. If any of these things happen when ITSS is closed, please
  follow up with them immediately the next business day. You MUST
  contact ITSS to resolve the issue if you are asking for any kind of
  leniency or extension.
\end{itemize}

\hypertarget{covid_policy}{%
\section{COVID policy}\label{covid_policy}}

\href{https://calstate.policystat.com/policy/11030468/latest/}{Per the
California State University Chancellor's Office policy, the Covid-19
vaccine and booster is required for students, faculty and staff, unless
you obtain an exemption from the university}. Currently, Chico State is
requiring everyone on campus to wear an approved face covering in all
indoor campus spaces. Accordingly, all students are required to wear an
appropriate face mask covering the nose and mouth in order to
participate in this course. Policies and requirements regarding COVID-19
are subject to change pursuant to campus, local, state and/or federal
guidelines.

Please note that dishonesty relating to the vaccination policy and/or
your failure to comply with any other COVID-19 related safety policy or
mandate, including the face covering requirement, may result in
disciplinary action against you through the office of Student Conduct,
Rights and Responsibilities, which can include suspension or expulsion
from the California State University system.

Individuals unable to wear a face covering due to a medical condition
should contact the \href{https://www.csuchico.edu/arc/}{Accessibility
Resource Center} by phone at 530-898-5959 or by email at
\href{mailto:arcdept@csuchico.edu}{\nolinkurl{arcdept@csuchico.edu}}.

\hypertarget{covid-policy-re-attendance}{%
\subsubsection{COVID policy re:
attendance:}\label{covid-policy-re-attendance}}

Attendance in this class is mandatory; if you do not attend class, you
will not pass. If, however, you are a campus student attending physical
class and you are symptomatic, please contact me (via email), do not
attend the in-person class, and contact the COVID hotline at
\textbf{(530)-898-2222} for additional direction. Also, make sure you
keep me updated as you learn more about your health status.

\hypertarget{attendance}{%
\section{Attendance Policy}\label{attendance}}

\textbf{Attendance and ongoing participation in sociology courses is
mandatory in all sociology classes and is essential to your success in
this course.} Only documented emergencies will constitute excused
absences or assignments. Documentation will only be accepted within one
week of your return to class. Please do not contact me about
non-emergency absences.
\textcolor{red}{\bf{You are allowed up to three (3) unexcused absences and anything more than that will affect your final grade. If you expect to miss class because of a religious observance, you will need to notify me beforehand. Finally, if you miss class, it is your responsibility to catch up.}}

\hypertarget{dropped-from-the-course}{%
\subsection{Dropped From The Course}\label{dropped-from-the-course}}

In accordance with the college drop policy, students who do not access
the class web site or submit the designated ``first assignments'' by the
due date may be dropped as a no show. Students who fail to turn in the
weekly assignments and/or participate in the discussion boards will be
considered ``absent'' and may be dropped from the class for ``excessive
absence.'' Students are responsible for officially dropping the class or
they will receive a letter grade based on their performance.

\begin{itemize}
\item
  \textbf{No Show Drop:} You must complete a designated discussion post,
  quiz, or practice activity by Friday of the first week of class or you
  may be dropped as a no-show. Students who do not complete \textbf{any}
  work in the first two weeks will be dropped.
\item
  \textbf{Excessive Absence Drop:} If more than two consecutive weeks of
  non-participation is observed by the instructor the student may be
  dropped. If you do not participate in each week's participation
  activities (during class, online activities, or Perusall) and complete
  at least one quiz or practice activity, you will be considered
  ``non-participating'' and subject to being dropped from the course.
\end{itemize}

\hypertarget{determination-of-final-grade}{%
\section{Determination of Final
Grade}\label{determination-of-final-grade}}

Table \ref{tab:grade_scale} displays the grading scale that is used to
determine a letter grade.

\renewcommand{\arraystretch}{1.5}

\begin{table}[!h]

\caption{\label{tab:grade_scale}Grading Scale}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{l|c|l}
\hline
\textbf{Grade} & \textbf{Range} & \textbf{Quality}\\
\hline
A & 93 - 100\% & Excellent Work\\
\hline
A- & 90 - 92\% & Nearly Excellent Work\\
\hline
B+ & 87 - 89\% & Very Good Work\\
\hline
B & 83 - 86\% & Good Work\\
\hline
B- & 80 - 82\% & Mostly Good Work\\
\hline
C+ & 77 - 79\% & Above Average Work\\
\hline
C & 73 - 76\% & Average Work\\
\hline
C- & 70 - 72\% & Mostly Average Work\\
\hline
D+ & 67 - 69\% & Below Average Work\\
\hline
D & 60 - 66\% & Poor Work\\
\hline
F & < 60\% & Failing Work\\
\hline
\end{tabular}
\end{table}

Table \ref{tab:weight_table} displays how your final grade will be
weighed according to the following components:

\renewcommand{\arraystretch}{1.5}

\begin{table}[!h]

\caption{\label{tab:weight_table}Course Requirements and Grading Policy}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lc}
\toprule
\textbf{Item} & \textbf{\% of Final Grade}\\
\midrule
Attendance \& Participation & 10 \%\\
Weekly Perusall Participation \& Discussion & 10 \%\\
Quizzes & 20 \%\\
Analytical Response Papers & 60 \%\\
TOTAL & 100 \%\\
\bottomrule
\end{tabular}
\end{table}

\textbf{Note regarding class workload:} This is a three (3) credit hour
class. You should expect to spend two hours outside of class for every
one hour in class. This time outside of class will be spent on reading,
assignments, and studying. This means you should plan on devoting six
hours of outside time per week to this course.

\hypertarget{attendance-and-class-participation-10-of-final-grade}{%
\subsection{Attendance and Class Participation (10\% of Final
Grade)}\label{attendance-and-class-participation-10-of-final-grade}}

The format of this course is an interactive, ``live'' hybrid lecture and
discussion with the objective of collaborative learning and analysis.
Participation in class discussion is necessary for your development as a
critical scholar and for your understanding of the course material.
Participation also includes consistent involvement in online interactive
activities. These activities will occur periodically during class
throughout the semester. This is a \textbf{required} course with
difficult reading material and, therefore, it is crucial to establish an
informed and critical discourse with each other over the material.
Participation includes contributions to class discussions either in
class or via class assignments. Participation also includes actively
listening, as well as sharing your ideas, criticisms, and frustrations
with course material. To ensure active participation, students must come
to class having read and taken notes on all material. Furthermore, you
are expected to contribute to discussions either in class or via class
assignments. Grading of all work is done with the expectation that
attendance and participation will be rewarded in the final grade. Also,
\protect\hyperlink{covid_policy}{see ``COVID Policy'' section} above if
you are symptomatic and an in-class student.

In addition to completing all of the assigned reading before each
designated day of the week (see reading schedule below and make sure you
attend class for the ongoing reading deadlines), you must critically
reflect on what is interesting/troubling/useful about what you have
read. You are expected to do this work on your own. Be prepared to offer
your questions, insights, and critique either via communication with me,
writing assignments and/or in conversation with other students.

\textbf{REMEMBER! Attendance is mandatory in all sociology classes (see
\protect\hyperlink{attendance}{Attendance Policy section} above). It is
also crucial to doing well in this class. In the context of this class,
attendance means COMPLETING ALL OF THE ASSIGNMENTS, QUIZZES, INDIVIDUAL
WORK, etc.}

\hypertarget{weekly-perusall-participation-10-of-final-grade}{%
\subsection{Weekly Perusall Participation (10\% of Final
Grade)}\label{weekly-perusall-participation-10-of-final-grade}}

For reading the primary texts (and not the textbook) we will use
\href{https://support.perusall.com/hc/en-us}{Perusall}, a social
annotation tool that allows students and their instructors to
collaboratively markup .pdf documents. Instead of only reading a
document and discussing it, Perusall brings discussion to text.

To start, register for a free Perusall account and enter the course
code: {[}Insert Code Here{]}

At the beginning of the semester, you will be assigned to groups in
Perusall, each comprised of around 10-12 students. After week 2, you
will be randomly placed into these groups and participate in
asynchronous group reading and discussion, covering any major theme(s)s
or issue(s) from the reading and lecture. You will each read and discuss
within your group forum. This means that you must not only do the
reading and annotate on your own, but you must ask and respond to one or
more questions within your group that are related to that week's
readings assignment(s) and lecture. Thus, you must interact in your
group forum with at least two (2) of your groupmate's posts. Your
contribution and annotations will be graded on a scale of 1 -- 3, with
higher scores indicating higher quality annotations and responses.
\textbf{Your annotations and responses to two or more groupmate's
annotations and questions are due on Friday by 8:00 PM. Discussion posts
and annotations will be given credit only if they are substantive and
follow all instructions.}

For reading assignments in Perusall, you will be evaluated based on the
following four criteria:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Quality: The more thoughtful the responses, the higher the score.
\item
  Quantity: Each student must submit at least seven (7) annotations in
  each reading document.
\item
  Timeliness: You must complete the reading assignment by Friday 11:30
  p.m.
\item
  Distribution: Are annotations made throughout the document? If most
  annotations are made in a single area, it indicates the student did
  not engage with the entire document. If annotations are distributed
  throughout the entire document, it indicates the student did engage
  with the reading in entirety.
\item
  Asking/Answering Questions: Ask and respond to each other's comments
  and questions in their group forums.
\end{enumerate}

\textbf{Common Question: What if I don't have any questions or
comments?} Elaborate on a specific topic, connect to personal experience
or perspective, extension to another topic or perspective, paraphrase
part of the text.

\hypertarget{quizzes}{%
\subsection{Quizzes (20\% of Final Grade; 4\% each)}\label{quizzes}}

Five (5) quizzes are required in this class. The first quiz will be a
syllabus quiz and will cover course policies and requirements. The
syllabus quiz will be posted on Canvas by the end of the first class and
must be completed by \textbf{11:59 p.m. on Friday September 2nd}. The
other four quizzes will cover theories, ideas, and concepts from the
course readings and lectures. \textbf{These four required reading
quizzes will be posted electronically on Thursday at 4:00 p.m. and must
be completed by 11:59 p.m. on Friday.} Each quiz will contain several
multiple choice questions based on course readings and lecture material.
These quizzes are designed to help you absorb the course readings and
lectures, and to provide you with the opportunity to assess your mastery
of the theories we are covering in the course.

\textbf{Important Note: Please keep in mind that your lowest quiz score
will not be counted when computing final grades. Instead, your highest
quiz score will be counted twice in replacement of your lowest quiz
score. All quizzes will be posted on Canvas and you will be provided
advanced notice.}

\hypertarget{writing_assignments}{%
\subsection{Four (4) Analytical Response Papers (60\% of Final Grade;
15\% each)}\label{writing_assignments}}

Four papers will be assigned for the semester. The required response
papers will answer either one or two questions posed by the professor
based on the course readings and lectures. These assignments will assess
knowledge of the course material, critical thinking skills, and writing
skills. The papers will require you to be analytical and to reflect
deeply on the theoretical works we will cover. Additional instructions
about the response papers will be distributed in class during the second
week of instruction. \textbf{Each paper must be turned in no later than
11:59 p.m. on the day that it is due.} Moreover, please also note that
you have options for each paper assignment; this means that for each
paper assignment you can choose to write between two sets of theories.
Additionally, you have the opportunity to re-write up to \textbf{two} of
your first three lower-scored analytical response papers for a higher
grade. If you decide to rewrite one or two lower-scored papers, these
will be due in class on \textbf{Tuesday, December 13, 2022 (our ``final
exam'' due date) no later than 11:59 p.m.}

\textbf{Due dates for all papers are listed below:}

\renewcommand{\arraystretch}{1.25}

\begin{longtable}[]{@{}lll@{}}
\toprule()
\textbf{Paper} & \textbf{Focus} & \textbf{Due Date} \\
\midrule()
\endhead
Paper \#1 & Structural Functionalist Theories & Sunday, Sept.~25 \\
& & \\
Paper \#2 & Symbolic Interactionism and the Work of & Sunday, Oct.~23 \\
& Erving Goffman; \textbf{OR}, Elite, Neo-Marxist, & \\
& and Critical Theories & \\
& & \\
Paper \#3 & Post-Structuralist Theory and the Work of & Sunday,
Nov.~20 \\
& Michel Foucault; \textbf{OR}, Pierre Bourdieu and & \\
& Theories of Social/ Cultural Reproduction & \\
& and Inequality & \\
& & \\
Paper \#4 & Theories of Race and Ethnicity; \textbf{OR}, & Tuesday,
Dec.~13 \\
& Feminist, Queer, and Intersectionality & \\
& Theories & \\
& & \\
\textbf{{[}Optional{]}} & Up to \textbf{Two} Re-Written Lower-Scored &
Tuesday, Dec.~13 \\
& Papers Chosen From The First Three & \\
& Analytical Papers Written & \\
\bottomrule()
\end{longtable}

\hypertarget{guidelines-for-papers}{%
\subsubsection{Guidelines for papers}\label{guidelines-for-papers}}

Papers have a word limit, approximately 1000 words (roughly 4
double-spaced pages); must be typed with 12-point font, 1-inch margins,
and Times New Roman font (11-point Arial font is also appropriate).
Proper grammar and APA citation of sources is expected. \textbf{No other
format will be accepted.}

\hypertarget{tips-and-tricks-for-good-writing}{%
\subsubsection{Tips and tricks for good
writing}\label{tips-and-tricks-for-good-writing}}

Use a citation management software to organize your papers and create
bibiliographies. My personal preference is
\href{https://www.zotero.org/}{Zotero} because it is free, open source,
and works across multiple operating systems. For information about other
citation management software that is available to CSU Chico students,
visit the Meriam Library
\href{https://libguides.csuchico.edu/c.php?g=432300\&p=2948649}{``Sample
Papers and Citation Tools'' page}.

Write and then revise. Ask for feedback from peers or wait until you
have some distance from your writing and then revise.

Prompt yourself with questions that have short, concrete answers.

\hypertarget{extra-credit-film-reviews-analyses-maximum-of-10-points5-points-per-analysis}{%
\subsection{Extra-Credit (Film Reviews \& Analyses) {[}Maximum of 10
Points/5 Points Per
Analysis{]}}\label{extra-credit-film-reviews-analyses-maximum-of-10-points5-points-per-analysis}}

Students will have the opportunity to earn extra credit in this course.
If you would like to earn up to 10 extra points maximum toward your
final course grade, you can write two 1-page (single-spaced) analytical
reviews and critiques of two films. The film analyses need to provide a
critical sociological review and analysis using one or more of the
theories or theorists covered in the course. A list of suggested films/
documentaries will be posted on Canvas by the end of the third week of
classes along with the guidelines for this assignment. \textbf{These
extra credit critiques should be concise and well-organized and argued;
the film analyses can be submitted at any time during the semester, but
no later than Friday December 9 by 11:59 p.m.}

\hypertarget{late-work-and-student-emergencies}{%
\subsection{Late Work and Student
Emergencies}\label{late-work-and-student-emergencies}}

Generally, late papers, past due participation in Perusall or
extra-credit work will \emph{not} be accepted in this course. However,
there are some important exceptions to this rule. Whenever unexpected
life challenges/emergencies or an illness interrupts your academic work,
other measures will apply. If you are ill or face an emergency, you are
asked to please notify the instructor immediately (via email or in
person), and provide documentation of what has occurred to justify
making-up your work or turning it in beyond it due date. Moreover, given
the current COVID-19 pandemic, I am aware that your situation can change
dramatically unexpectedly.
\textbf{\textcolor{red}{If you are facing any personal, medical, financial or other challenges that impact your academic work, please inform me right away and we will work out a solution to your problem. I will do my best to accommodate your situation and allow you to complete your work at a later time if you missed a deadline.}
\textcolor{red}{However, the longer you wait, the less likely I am to accept a late assignment. Furthermore, I reserve the right to refuse any late work thus, keeping the lines of communication open is your best bet if you fall a little behind on an assignment.}}

The instructor's policy regarding late work is to give any student who
is ill or has faced a \textbf{documented medical/personal emergency} the
opportunity to make up his/her academic work \textbf{within one week of
the absence.} Therefore, it is imperative that you discuss with the
instructor any emergencies and/or problems in order to assist you in
completing your coursework.
\textcolor{red}{\bf{Please also note that if you foresee being absent due to a conflict with religious observance(s), you must notify the instructor of your prospective absence during the first week of classes.}}

If you have any questions, do not hesitate to discuss these issues with
the instructor in person or via Canvas.

\hypertarget{getting-help-and-communicating-with-your-professor}{%
\section{Getting Help And Communicating With Your
Professor}\label{getting-help-and-communicating-with-your-professor}}

Remember, your professor is here to help you gain a rich understanding
of the material. So, it is important to be connected to your instructor
and seek help whenever you need it. However, it is primarily your
responsibility to seek help when you need it. Use the following methods
to get in touch and/or ask questions.

\hypertarget{communication-policy}{%
\subsection{Communication policy}\label{communication-policy}}

When contacting your about the course, please send message through
``Message Your Professor'' in Canvas. I check messages three times per
day, Monday thru Friday, between 9:00 AM and 6:00 PM. Please allow up to
24-48 hours for a response during the week. If you contact on the
weekend, expect a reply the following Monday.

\begin{itemize}
\item
  Requesting help: If you miss a class meeting, you should\ldots{}

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \tightlist
  \item
    First, look on the course website for material you missed.
  \item
    Second, if you need help understanding the material, you should
    contact your classmate (either via direct email or Canvas discussion
    board).
  \item
    Third, if you still find it difficult, find some time to chat with
    me during office hours
  \end{enumerate}
\item
  Requesting a 1-on-1, non-office-hour Zoom meeting:

  \begin{quote}
  If, after you've looked over the material yourself and reached out to
  classmates, you still need help but cannot attend office hours, you
  may email me to request a virtual Zoom meeting. For non-office-hour
  zoom meetings, I require at least a minimum of one-week's notice.
  \end{quote}
\item
  On-line communication

  \begin{quote}
  I require that all communication be done in a respectful, courteous,
  and professional manner. When in doubt, always err in these
  directions; for example, aim for being slightly more courteous than
  you may think you need to be. Nobody will object to an extra
  ``please'' or ``thank you.'' Always take a few minutes to read what
  you have written before posting a comment or sending an email -- pause
  and think -- could what you have written be construed as
  disrespectful, impolite, or snappy? When in doubt, re-think your words
  and tone, and re-calibrate your message. We may not always agree but
  disagreeing while simultaneously showing respect and courtesy toward
  someone is a skill that will serve you well throughout your life and
  in many contexts. Always make criticism constructive and not personal.
  If you disagree with someone, they should not feel personally
  attacked. Keep the ideas separate from the person. I will always keep
  these principles in mind when communicating with you -- please do the
  same toward me and your fellow students.
  \end{quote}
\end{itemize}

\textbf{I reserve the right to penalize individuals who do not
demonstrate these basic principles in their communications.}

\hypertarget{powerpoint-lecture-slides-availability}{%
\section{Powerpoint Lecture Slides
Availability:}\label{powerpoint-lecture-slides-availability}}

Please note that course is taught in a ``synchronous manner'' which
means that lectures will be delivered ``live''. \textbf{Each week the
PowerPoint lecture slides used in each class meeting will be posted on
Canvas (in the ``Modules'' section) on the following Friday.}

\hypertarget{use-of-lecture-material-powerpoint-lecture-slides-and-electronic-readings}{%
\subsection{Use of Lecture Material, PowerPoint Lecture Slides, and
Electronic
Readings:}\label{use-of-lecture-material-powerpoint-lecture-slides-and-electronic-readings}}

It is most important that you know that
\textcolor{red}{\bf{all} course materials (i.e, the course syllabus, assignments, handouts, exams, etc.) are the instructor’s property. Course readings, on the other hand, are the property of their writers and editors, and together, should be used only by students enrolled in this course. These materials should not be distributed or used beyond the member of this course. If you do, this will constitute a major legal violation with serious penalties.}
These materials are available to you to facilitate your own personal
learning in this class. Sale of course or reproduction of course
materials, including lecture content and information, are strictly
prohibited. All class material, particularly lectures, cannot be further
reproduced. Reproduction of audio or video of zoom lectures or
powerpoint slides by students or anyone else is \textbf{\emph{strictly
prohibited}} under any circumstances.
\textcolor{red}{\bf{Professor Jacinto reserves the right to take academic penalty measures and/or legal action if you are found in violation of any of the expectations stated here.}}

\hypertarget{creating-a-safe-and-inclusive-learning-environment}{%
\section{Creating a Safe and Inclusive Learning
Environment}\label{creating-a-safe-and-inclusive-learning-environment}}

\hypertarget{mandatory-reporting}{%
\subsection{Mandatory Reporting}\label{mandatory-reporting}}

As an instructor, one of my responsibilities is to help create a safe
learning environment on our campus. I also have a mandatory reporting
responsibility related to my role as an instructor. It is my goal that
you feel able to share information related to your life experiences in
classroom discussions, in your written work, and in our one-on-one
meetings. I will seek to keep information you share private to the
greatest extent possible. However, I am legally required to share
information regarding sexual misconduct with the University. Students
may speak to someone confidentially by contacting the
\href{https://www.csuchico.edu/counseling/}{Counseling and Wellness
Center} (530-898-6345) or
\href{https://www.csuchico.edu/safeplace/}{Safe Place} (530-898-3030).
Information on campus reporting obligations and other Title IX related
resources are available here: \url{https://www.csuchico.edu/title-ix/}

\hypertarget{statement-of-commitment-to-diversity-equity-and-inclusion}{%
\subsection{Statement of Commitment to Diversity, Equity, and
Inclusion}\label{statement-of-commitment-to-diversity-equity-and-inclusion}}

Education is transformative, and open intellectual inquiry is the
foundation of a university education and a democratic society. In the
spirit of shared humanity and concern for our community and world, the
faculty of Chico State's Sociology Department celebrate diversity as
central to our mission and affirm our solidarity with those individuals
and groups most at risk. In line with our departmental goals, we disavow
all racism, xenophobia, homophobia, sexism, Islamophobia, anti-Semitism,
classism, ableism, and hate speech or actions that attempt to silence,
threaten, and degrade others.

As educators, we affirm that language and texts, films and stories help
us to understand the experiences of others whose lives are different
from ours. We value critical reasoning, evidence-based arguments,
self-reflection, and the imagination. Building on these capacities, we
hope to inspire empathy, social and environmental justice, and an
ethical framework for our actions. We advocate for a diverse campus,
community, and nation inclusive of racial minorities, women, immigrants,
the LGBTQ+ community, and people of all religious faiths.

\hypertarget{statement-of-respect-for-diversity-in-learning-styles-perspectives-and-backgrounds}{%
\subsection{Statement of Respect for Diversity in Learning Styles,
Perspectives, and
Backgrounds}\label{statement-of-respect-for-diversity-in-learning-styles-perspectives-and-backgrounds}}

Each of us arrives in the classroom with a multitude of life
experiences, and we all learn in different ways. In designing this
class, my intent has been to provide many different methods to practice
and learn to support these different learning styles. In addition, to
learn about applying sociological perspectives to social issues, we will
use a variety of example to demonstrate their applicability. Some
examples will be simple and often use `made-up' scenarios, while others
deal with real life events and experiences about important social
issues. It is my hope that all materials in the class are respectful to
people from all backgrounds including diversity in sex/gender,
sexuality, disability, age, socioeconomic status, ethnicity/race,
immigration status, veteran status, religion, and culture. I invite your
feedback on this, and your suggestions are always welcome.

\hypertarget{undocumented-daca-or-ab-540-immigrant-students}{%
\subsection{Undocumented, DACA, or AB-540 Immigrant
Students}\label{undocumented-daca-or-ab-540-immigrant-students}}

As an educator, I strive to make courses accessible to all students
regardless of immigration status. If your status presents obstacles to
engaging in specific activities or fulfilling specific criteria, you may
request confidential accommodations. You may consult with the
\href{https://www.csuchico.edu/diversity/}{Office of Equity and
Diversity} or the \href{https://www.csuchico.edu/dreamcenter/}{Dream
Center} for examples of possible accommodations. Such arrangements will
not jeopardize your student status, your financial aid, or any other
part of your residence. Please advise me if and when you feel
comfortable during the semester so that I may make appropriate
alterations as needed.

\textbf{Note:} For all students addressing undocumented immigration as a
category of analysis in class, do not use the word ``illegal(s)'' in a
discussion. The term ``illegal(s)'' promotes a culture of intolerance
and violence toward foreign nationals and undocumented immigrants. A
more accurate and non-offensive term is ``undocumented immigrant(s).''
The use of this language signifies respect to the population addressed
and reflects our campus's most basic values of diversity and civility in
academic discourse.

\hypertarget{statement-on-eliminating-anti-blackness}{%
\subsection{Statement on Eliminating
Anti-Blackness}\label{statement-on-eliminating-anti-blackness}}

Faculty at CSU Chico strive to create an environment that supports
meaningful dialogue grounded in research, academic inquiry, and mutually
respectful relations. We also strive to remain conscious of and
attentive to the damage that anti-Blackness does to the lives of our
students, faculty, staff, administrators, and their related communities.
As such, faculty at CSU Chico denounce anti-Blackness and racial
violence in all forms and stand in solidarity with Black communities in
the fight for racial justice, equality, and equity. We pledge to remake
our institution as one that values, honors, and supports Black lives. We
recognize the impact of anti-Blackness on our students, and we invite
them to dialogue with their professors as we work to make our classrooms
anti-racist and dignity-affirming spaces.

\hypertarget{lgbtq-equality-statement}{%
\subsection{LGBTQ+ Equality Statement}\label{lgbtq-equality-statement}}

I am firmly committed to diversity and equality in all areas of campus
life, including specifically members of the LGBTQ+ community. In this
class I will work to promote an anti-discriminatory environment where
everyone feels safe and welcome. I recognize that discrimination can be
direct or indirect and take place at both institutional and personal
levels. I unequivocally believe that such discrimination is unacceptable
and I am committed to providing equality of opportunity for all by
eliminating any and all discrimination, harassment, bullying, or
victimization. The success of this policy relies on the support and
understanding of everyone in this class. We all have a responsibility
not to be offensive to each other, or to participate in, or condone
harassment or discrimination of any kind.

\hypertarget{mental-health}{%
\subsection{Mental health}\label{mental-health}}

Being a university student is stressful and can negatively impact mental
health. The \href{https://www.csuchico.edu/counseling/}{WildCat
Counseling Center} offers free counseling services to regularly enrolled
students at California State University, Chico. There are a wide variety
of reasons students seek counseling:

\begin{itemize}
\tightlist
\item
  Resolving personal problems or conflicts.
\item
  Seeking clarification and support in making important life decisions.
\item
  Experiencing an emotional crisis due to a traumatic incident or a
  series of incidents.
\item
  Help in developing personal survival skills necessary to achieve
  personal goals.
\end{itemize}

\textcolor{ForestGreen}{\bf{Absences for mental health reasons are excused but the professor should be notified immediately (within 48 - 72 hours of absence) to prevent any penalty on your final grade.}}

\hypertarget{other-course-policies}{%
\section{Other Course Policies}\label{other-course-policies}}

\begin{itemize}
\item
  Unless you have a documented emergency, there will be no substitutions
  for assignments, quizzes, or papers. A missed assignment, quiz, or
  paper will result in a zero. Incomplete grades (or an ``I'' grade) are
  rare, and will be given at the discretion of the professor.
\item
  ``Pet Peeves'':

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \tightlist
  \item
    Asking to be excused from rules that all classmates are following.
  \item
    \textbf{Inappropriate or disruptive behavior will not be tolerated.
    If this behavior persists, the student will be reported to the
    Dean's Office.}
  \end{enumerate}
\item
  As mentioned in the \protect\hyperlink{writing_assignments}{``Four (4)
  Analytical Response Papers'' section} above, all papers must be
  12-point Times New Roman font (or 11-point Arial font), double-spaced,
  and have 1'' margins. Students' names are to be in the upper right
  hand corner with the date and student ID number included; also,
  include page numbers in the bottom right hand corner of the paper.
  Excessive spacing beyond this identification will result in the
  deduction of points. Finally, follow APA citation style, and give full
  references. For help with formatting citations and bibliographies,
  visit the ``Citing Sources'' page in Meriam Library's website:
  \url{https://libguides.csuchico.edu/cite}
\item
  When there is evidence that a student has committed plagiary, copied
  the work of others, allowed others to copy their work, cheated on a
  quiz, altered class material or scores, or has inappropriate
  possession of quizzes, or sensitive material, the incident will be
  investigated by Student Judicial Affairs.
  \textcolor{red}{\bf{The consequences for academic dishonesty are severe, including receiving an “F” in the course. No exceptions.}}
\item
  All written work will be assessed on content, depth, logic, and
  quality of written expression.
\item
  Students are responsible for handling the necessary paperwork for
  adding or dropping this class.
  \textcolor{red}{\bf{If a student does not withdraw, and does not attend class or complete required work, an “F” or “WU” will be reported for the final grade. Instructors may drop a student who does not attend the first two classes.}}
\end{itemize}

\hypertarget{university-policies-and-campus-resources}{%
\section{University Policies and Campus
Resources}\label{university-policies-and-campus-resources}}

\hypertarget{academic-integrity}{%
\subsection{Academic Integrity}\label{academic-integrity}}

Academic honesty and integrity are core values in this class and at
Chico State. Acts of plagiarism, dishonesty, and misrepresentation of
work are just a few examples of inappropriate behavior in this class.
Breeches in academic honesty and integrity will be submitted to the
Office of Student Conduct, Rights and Responsibilities for sanction.
Additionally, breaches in academic honesty will result in a failing
grade for the assignment to which the breach was committed, or, at the
discretion of the instructor, a failing grade for the course. For more
information about academic honesty and integrity, please visit
\url{http://www.csuchico.edu/prs/EMs/2004/04-036.shtml}.

\hypertarget{student-services}{%
\subsection{Student Services}\label{student-services}}

Student services are designed to assist students in the development of
their full academic potential and to motivate them to become
self-directed learners. Students can find support for services such as
skills assessment, individual or group tutorials, subject advising,
learning assistance, summer academic preparation and basic skills
development. Student services information can be found on the current
students page of the \href{https://www.csuchico.edu/sa/}{CSU Chico web
site}.

\hypertarget{student-learning-center}{%
\subsection{Student Learning Center}\label{student-learning-center}}

The mission of the Student Learning Center (SLC) is to provide services
that will assist CSU, Chico students to become independent learners. The
SLC prepares and supports students in their college course work by
offering a variety of programs and resources to meet student needs. The
SLC facilitates the academic transition and retention of students from
high schools and community colleges by providing study strategy
information, content subject tutoring, and supplemental instruction. I
suggest you visit the \href{https://www.csuchico.edu/slc/}{Student
Learning Center web site}.

\hypertarget{writing-center}{%
\subsection{Writing Center}\label{writing-center}}

Over the course of this semester, seek help at the Writing Center if you
would like additional guidance and critique. You can access the Writing
Center at
\href{https://www.csuchico.edu/slc/writing-center/index.shtml}{at their
website}. During graduate school, I found workshops and writing groups
at the Writing Center on campus to be helpful in building my motivation
and teaching me new strategies for writing efficiently. While it is not
a requirement, I nevertheless urge you to meet with a writing tutor to
review a writing assignment at least once during the semester.

\hypertarget{americans-with-disabilities-act}{%
\subsection{Americans with Disabilities
Act}\label{americans-with-disabilities-act}}

If you need course adaptations or accommodations because of a disability
or chronic illness, or if you need to make special arrangements in case
the building must be evacuated, please make an appointment with me as
soon as possible, or see me during office hours. Please also contact
Accessibility Resource Center (ARC) as they are the designated
department responsible for approving and coordinating reasonable
accommodations and services for students with disabilities. ARC will
help you understand your rights and responsibilities under the Americans
with Disabilities Act and provide you further assistance with requesting
and arranging accommodations. See contact info below:

\begin{quote}
\textbf{Accessibility Resource Center}\\
Student Services Center 170\\
530-898-5959\\
\href{mailto:arcdept@csuchico.edu}{\nolinkurl{arcdept@csuchico.edu}}\\
\url{https://www.csuchico.edu/arc/}
\end{quote}

\hypertarget{food-insecurity}{%
\subsection{Food insecurity}\label{food-insecurity}}

CSU Chico recognizes food and housing insecurity as a concern for many
people. Students who have difficulty securing adequate food or housing
have long and short term resources available at Chico State. Students
are encouraged to contact the
\href{https://www.csuchico.edu/chc/}{Center for Healthy Communities} or
530-898-5323 for assistance in applying for CalFresh benefits for long
term assistance with food access. For emergency food supplies, CalFresh
application help, and emergency housing information, students are
encouraged to visit the
\href{https://www.csuchico.edu/basic-needs/pantry.shtml}{Wildcat Food
Pantry}.

\hypertarget{final-thoughts}{%
\section{Final thoughts}\label{final-thoughts}}

This document is a roadmap for our semester. We learn about social
theory together and its applicability towards understanding our
environment. Like all your classes, you will get out what you put into
this course. Asking for help from one another and your instructors is
important, don't be afraid to ask a question about something you don't
know or if you want to check your knowledge about something you think
you know. Do not wait to ask for help! We are all here to learn; it is
not a competition.

\textbf{If this document is updated, a copy will be supplied to you via
Canvas and changes will be announced in class.}

\newpage

\renewcommand{\arraystretch}{1.25}

\hypertarget{course-and-reading-schedule}{%
\section{Course and Reading
Schedule}\label{course-and-reading-schedule}}

The following is a tentative schedule for the Fall 2022 semester. It
lists readings and due dates, and \textbf{may be subject to change.} Any
changes will be announced in class and will be shown in Canvas
immediately. Use this information to schedule accordingly. If you miss
class, it is your responsibility to find out if any scheduling changes
were made in class.

Table \ref{tab:course_schedule} displays the course schedule for the
Fall 2022 semester. It lists the days and weeks we will meet for
lecture. \textbf{We will not meet during Fall Break (Nov.~21-25).}

\begin{table}[!h]

\caption{\label{tab:course_schedule}Course Schedule.}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{llccc}
\toprule
\textbf{Date} & \textbf{Weekday} & \textbf{Class} & \textbf{Week} & \textbf{Lecture}\\
\midrule
2022-08-23 & Tuesday & 1 & 1 & 1\\
2022-08-25 & Thursday & 2 & 1 & 2\\
2022-08-30 & Tuesday & 3 & 2 & 3\\
2022-09-01 & Thursday & 4 & 2 & 4\\
2022-09-06 & Tuesday & 5 & 3 & 5\\
2022-09-08 & Thursday & 6 & 3 & 6\\
2022-09-13 & Tuesday & 7 & 4 & 7\\
2022-09-15 & Thursday & 8 & 4 & 8\\
2022-09-20 & Tuesday & 9 & 5 & 9\\
2022-09-22 & Thursday & 10 & 5 & 10\\
2022-09-27 & Tuesday & 11 & 6 & 11\\
2022-09-29 & Thursday & 12 & 6 & 12\\
2022-10-04 & Tuesday & 13 & 7 & 13\\
2022-10-06 & Thursday & 14 & 7 & 14\\
2022-10-11 & Tuesday & 15 & 8 & 15\\
2022-10-13 & Thursday & 16 & 8 & 16\\
2022-10-18 & Tuesday & 17 & 9 & 17\\
2022-10-20 & Thursday & 18 & 9 & 18\\
2022-10-25 & Tuesday & 19 & 10 & 19\\
2022-10-27 & Thursday & 20 & 10 & 20\\
2022-11-01 & Tuesday & 21 & 11 & 21\\
2022-11-03 & Thursday & 22 & 11 & 22\\
2022-11-08 & Tuesday & 23 & 12 & 23\\
2022-11-10 & Thursday & 24 & 12 & 24\\
2022-11-15 & Tuesday & 25 & 13 & 25\\
2022-11-17 & Thursday & 26 & 13 & 26\\
2022-11-29 & Tuesday & 27 & 15 & 27\\
2022-12-01 & Thursday & 28 & 15 & 28\\
2022-12-06 & Tuesday & 29 & 16 & 29\\
2022-12-08 & Thursday & 30 & 16 & 30\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{tentative-reading-and-assignments-schedule}{%
\subsection{Tentative Reading and Assignments
Schedule}\label{tentative-reading-and-assignments-schedule}}

Readings we will cover are listed below.
\textcolor{red}{\bf{Note that the professor reserves the right to change the readings and assignment due dates below based on new and developing information about what would best serve my students.}}
Changes in the syllabus will be highlighted in
\colorbox{Cyan}{\bf{cyan.}} In the event that a reading has not been
made available in a way that you can access it on Canvas or Perusall,
please email me immediately so the professor may repost the
reading/assignment in time for you to complete it before the next class
period. You will also be immediately notified when there the due date of
an assignment has changed.

\emph{These are questions you should consider as you complete each
reading:} What are the authors' main objectives/research questions? What
methods, if any, did the author use to explore this question? What are
the author's main conclusions? How do the readings build upon or
challenge other works we have read thus far? Answering these questions
on your own will better prepare you for quizzes and writing assignments.

\hypertarget{course-schedule}{%
\section{COURSE SCHEDULE}\label{course-schedule}}

\hypertarget{week-01-0823---0825-introduction-and-overview-of-course}{%
\subsection{WEEK 01, 08/23 - 08/25: Introduction and Overview of
Course}\label{week-01-0823---0825-introduction-and-overview-of-course}}

\bigbreak
\hrule

\hypertarget{week-02-0830---0901-structural-functionalist-theories-i}{%
\subsection{WEEK 02, 08/30 - 09/01: Structural Functionalist Theories,
I}\label{week-02-0830---0901-structural-functionalist-theories-i}}

\textbf{Required Readings:}

\begin{itemize}
\item
  Dillon M (2020). \emph{Introduction to Sociological Theory: Theorists,
  Concepts, and their Applicabilityto the Twenty-First Century}, 3
  edition. Wiley-Blackwell, Hoboken, NJ. ISBN 978-1-119-41091-1.
  \textcolor{BrickRed}{\bf{[Read: Chapter 4]}}
\item
  Parsons T (2017). ``The school class as a social system: Some of its
  functions in American society.'' In \emph{Exploring Education},
  151-164. Routledge. \colorbox{Goldenrod}{\bf{[E-Posting]}}
\end{itemize}

\textbf{Assignments Due:}

\begin{itemize}
\tightlist
\item
  Weekly Perusall Participation
\end{itemize}

\bigbreak
\hrule

\hypertarget{week-03-0906---0908-structural-functionalist-theories-ii}{%
\subsection{WEEK 03, 09/06 - 09/08: Structural Functionalist Theories,
II}\label{week-03-0906---0908-structural-functionalist-theories-ii}}

\textbf{Required Readings:}

\begin{itemize}
\item
  Merton RK (1938). ``Social Structure and Anomie.'' \emph{American
  Sociological Review}, \emph{3}, 672-682.
  \colorbox{Goldenrod}{\bf{[E-Posting]}}
\item
  Davis K, Moore WE (1945). ``Some Principles of Stratification.''
  \emph{American Sociological Review}, \emph{10}(2), 242-249.
  \colorbox{Goldenrod}{\bf{[E-Posting]}}
\end{itemize}

\textbf{Assignments Due:}

\begin{itemize}
\tightlist
\item
  Weekly Perusall Participation
\end{itemize}

\bigbreak
\hrule

\hypertarget{week-04-0913---0915-symbolic-interactionism-the-work-of-erving-goffman-i}{%
\subsection{WEEK 04, 09/13 - 09/15: Symbolic Interactionism \& the Work
of Erving Goffman,
I}\label{week-04-0913---0915-symbolic-interactionism-the-work-of-erving-goffman-i}}

\textbf{Required Readings:}

\begin{itemize}
\item
  Dillon M (2020). \emph{Introduction to Sociological Theory: Theorists,
  Concepts, and their Applicabilityto the Twenty-First Century}, 3
  edition. Wiley-Blackwell, Hoboken, NJ. ISBN 978-1-119-41091-1.
  \textcolor{BrickRed}{\bf{[Read: Chapter 8]}}
\item
  Goffman E (2018). ``Stigma And Social Identity.'' In \emph{Deviance \&
  Liberty}, 1 edition, 24-31. Routledge. ISBN 978-0-203-79334-3, doi:
  10.4324/9780203793343-4 (URL:
  \url{https://doi.org/10.4324/9780203793343-4}), \textless URL:
  \url{https://www.taylorfrancis.com/books/9781351522373/chapters/10.4324/9780203793343-4}\textgreater.
  \colorbox{Goldenrod}{\bf{[E-Posting]}}
\end{itemize}

\textbf{Assignments Due:}

\begin{itemize}
\tightlist
\item
  Weekly Perusall Participation
\end{itemize}

\bigbreak
\hrule

\hypertarget{week-05-0920---0922-the-work-of-erving-goffman-ii}{%
\subsection{WEEK 05, 09/20 - 09/22: The Work of Erving Goffman,
II}\label{week-05-0920---0922-the-work-of-erving-goffman-ii}}

\textbf{Required Readings:}

\begin{itemize}
\tightlist
\item
  Goffman E (1959). \emph{The Presentation of Self in Everyday Life}.
  Anchor Books. ISBN 0-385-09402-7.
  \colorbox{Goldenrod}{\bf{[E-Posting: Read: Introduction and Chapter 1 Only]}}
\end{itemize}

\textbf{Assignments Due:}

\begin{itemize}
\tightlist
\item
  Weekly Perusall Participation
\item
  \textbf{Paper \#1 due by Sunday 11:59 p.m.}
\item
  \textbf{Quiz \#1 must be completed by Friday 11:59 p.m.}
\end{itemize}

\bigbreak
\hrule

\hypertarget{week-06-0927---0929-power-elite-theories}{%
\subsection{WEEK 06, 09/27 - 09/29: Power Elite
Theories}\label{week-06-0927---0929-power-elite-theories}}

\textbf{Required Readings:}

\begin{itemize}
\item
  Mills CW (1956). ``The Power Elite.'' In \emph{The Power Elite}, New
  edition. Oxford University Press, New York. ISBN 0-19-513354-4.
  \colorbox{Goldenrod}{\bf{[E-Posting]}}
\item
  Molotoch H (1976). ``The City as a Growth Machine: Toward a Political
  Economy of Place.'' \emph{American Journal of Sociology},
  \emph{82}(2), 309-332. \colorbox{Goldenrod}{\bf{[E-Posting]}}
\end{itemize}

\textbf{Assignments Due:}

\begin{itemize}
\tightlist
\item
  Weekly Perusall Participation
\end{itemize}

\bigbreak
\hrule

\hypertarget{week-07-1004---1006-neo-marxism-and-critical-theories}{%
\subsection{WEEK 07, 10/04 - 10/06: Neo-Marxism and Critical
Theories}\label{week-07-1004---1006-neo-marxism-and-critical-theories}}

\textbf{Required Readings:}

\begin{itemize}
\item
  Gramsci A (1971). ``Selections From The Prison Notebooks.'' In Hoare
  Q, Smith GN (eds.), \emph{Selections From The Prison Notebooks}, 1
  edition. International Publishers, New York.

  \colorbox{Goldenrod}{\bf{[E-Posting: Read: 238-276 only]}}
\item
  Horkheimer M, Adorno TW (2017). ``The Culture Industry: Enlightenment
  as Mass Deception.'' In \emph{Karl Marx}. Routledge.
  \colorbox{Goldenrod}{\bf{[E-Posting}}
\end{itemize}

\textbf{Assignments Due:}

\begin{itemize}
\tightlist
\item
  Weekly Perusall Participation
\end{itemize}

\bigbreak
\hrule

\hypertarget{week-08-1011---1013-post-structuralism-the-work-of-michel-foucault-i}{%
\subsection{WEEK 08, 10/11 - 10/13 Post-Structuralism \& the Work of
Michel Foucault,
I}\label{week-08-1011---1013-post-structuralism-the-work-of-michel-foucault-i}}

\textbf{Required Readings:}

\begin{itemize}
\item
  Dillon M (2020). \emph{Introduction to Sociological Theory: Theorists,
  Concepts, and their Applicabilityto the Twenty-First Century}, 3
  edition. Wiley-Blackwell, Hoboken, NJ. ISBN 978-1-119-41091-1.
  \textcolor{BrickRed}{\bf{[Read: Chapter 11: 343-352 only]}}
\item
  Foucault M (1982). ``The Subject and Power.'' \emph{Critical Inquiry},
  \emph{8}(4), 777-795. \colorbox{Goldenrod}{\bf{[E-Posting]}}
\end{itemize}

\textbf{Assignments Due:}

\begin{itemize}
\tightlist
\item
  Weekly Perusall Participation
\end{itemize}

\bigbreak
\hrule

\hypertarget{week-09-1018---1020-the-work-of-michel-foucault-ii}{%
\subsection{WEEK 09, 10/18 - 10/20: The Work of Michel Foucault,
II}\label{week-09-1018---1020-the-work-of-michel-foucault-ii}}

\textbf{Required Readings:}

\begin{itemize}
\item
  Foucault M (2022). ````Panopticism'' from ``Discipline \& Punish: The
  Birth of the Prison''.'' \emph{MICHEL FOUCAULT}, 13.
  \colorbox{Goldenrod}{\bf{[E-Posting]}}
\item
  Foucault M (1978). \emph{The history of sexuality}, 1st American ed
  edition. Pantheon Books, New York. ISBN 978-0-394-41775-2.
  \colorbox{Goldenrod}{\bf{[E-Posting: Read: 15-73 only]}}
\end{itemize}

\textbf{Assignments Due:}

\begin{itemize}
\tightlist
\item
  Weekly Perusall Participation
\item
  \textbf{Paper \#2 due by Sunday 11:59 p.m.}
\item
  \textbf{Quiz \#2 must be completed by Friday 11:59 p.m.}
\end{itemize}

\bigbreak
\hrule

\hypertarget{week-10-1025---1027-theories-of-socialcultural-reproduction-inequality-the-work-of-pierre-bourdieu-i}{%
\subsection{WEEK 10, 10/25 - 10/27: Theories of Social/Cultural
Reproduction \& Inequality: The Work of Pierre Bourdieu,
I}\label{week-10-1025---1027-theories-of-socialcultural-reproduction-inequality-the-work-of-pierre-bourdieu-i}}

\textbf{Required Readings:}

\begin{itemize}
\item
  Dillon M (2020). \emph{Introduction to Sociological Theory: Theorists,
  Concepts, and their Applicabilityto the Twenty-First Century}, 3
  edition. Wiley-Blackwell, Hoboken, NJ. ISBN 978-1-119-41091-1.
  \textcolor{BrickRed}{\bf{[Read: Chapter 13]}}
\item
  Bourdieu P (1994). ``Structures, Habitus, Power: Basis for a Theory of
  Symbolic Power.'' In Dirks NB, Eley G, Ortner SB (eds.),
  \emph{Culture/Power/History: A Reader in Contemporary Social Theory},
  volume 12, 155-199. Princeton University Press. \textless URL:
  \url{https://doi.org/10.2307/j.ctv1ddd17k}\textgreater.
  \colorbox{Goldenrod}{\bf{[E-Posting]}}
\end{itemize}

\textbf{Assignments Due:}

\begin{itemize}
\tightlist
\item
  Weekly Perusall Participation
\end{itemize}

\bigbreak
\hrule

\hypertarget{week-11-1101---1103-the-work-of-pierre-bourdieu-ii}{%
\subsection{WEEK 11, 11/01 - 11/03: The Work of Pierre Bourdieu,
II}\label{week-11-1101---1103-the-work-of-pierre-bourdieu-ii}}

\begin{itemize}
\tightlist
\item
  Bourdieu P (1991). \emph{Language and symbolic power}, 1 edition.
  Polity Press, Cambridge. ISBN 978-0-7456-0097-0 978-0-7456-1034-4.
  \colorbox{Goldenrod}{\bf{[E-Posting: Read: pp. 43-65 and 163-170]}}
\end{itemize}

\textbf{Assignments Due:}

\begin{itemize}
\tightlist
\item
  Weekly Perusall Participation
\end{itemize}

\bigbreak
\hrule

\hypertarget{week-12-1108---1110-theories-of-race-ethnicity-i}{%
\subsection{WEEK 12, 11/08 - 11/10: Theories of Race \& Ethnicity,
I}\label{week-12-1108---1110-theories-of-race-ethnicity-i}}

\textbf{Required Readings:}

\begin{itemize}
\item
  Omi M, Winant H (2020). ``Racial Formation.'' In \emph{The New Social
  Theory Reader}, 405-415. Routledge.
  \colorbox{Goldenrod}{\bf{[E-Posting]}}
\item
  Feagin J, Elias S (2013). ``Rethinking Racial Formation Theory: A
  Systemic Racism Critique.'' \emph{Ethnic and Racial Studies},
  \emph{36}(6), 931-960. doi: 10.1080/01419870.2012.669839 (URL:
  \url{https://doi.org/10.1080/01419870.2012.669839}).
  \colorbox{Goldenrod}{\bf{[E-Posting]}}
\item
  Winant H (2000). ``Race and Race Theory.'' \emph{Annual Review of
  Sociology}, \emph{26}(1), 169-185. ISSN 0360-0572, 1545-2115, doi:
  10.1146/annurev.soc.26.1.169 (URL:
  \url{https://doi.org/10.1146/annurev.soc.26.1.169}), \textless URL:
  \url{https://www.annualreviews.org/doi/10.1146/annurev.soc.26.1.169}\textgreater.
  \colorbox{Goldenrod}{\bf{[E-Posting]}}
\end{itemize}

\textbf{Assignments Due:}

\begin{itemize}
\tightlist
\item
  Weekly Perusall Participation
\end{itemize}

\bigbreak
\hrule

\hypertarget{week-13-1115---1117-theories-of-race-ethnicity-ii}{%
\subsection{WEEK 13, 11/15 - 11/17: Theories of Race \& Ethnicity,
II}\label{week-13-1115---1117-theories-of-race-ethnicity-ii}}

\textbf{Required Readings:}

\begin{itemize}
\item
  Lee J, Bean FD (2004). ``America's Changing Color Lines: Immigration,
  Race/Ethnicity, and Multiracial Identification.'' \emph{Annual Review
  of Sociology}, \emph{30}(1), 221-242. ISSN 0360-0572, 1545-2115, doi:
  10.1146/annurev.soc.30.012703.110519 (URL:
  \url{https://doi.org/10.1146/annurev.soc.30.012703.110519}),
  \textless URL:
  \url{https://www.annualreviews.org/doi/10.1146/annurev.soc.30.012703.110519}\textgreater.
  \colorbox{Goldenrod}{\bf{[E-Posting]}}
\item
  Wilson WJ (2011). ``The Declining Significance of Race: Revisited \&
  Revised.'' \emph{Daedalus}, \emph{140}(2), 55-69. ISSN 0011-5266, doi:
  10.1162/DAED\_a\_00077 (URL:
  \url{https://doi.org/10.1162/DAED_a_00077}), \textless URL:
  \url{https://doi.org/10.1162/DAED_a_00077}\textgreater.
  \colorbox{Goldenrod}{\bf{[E-Posting]}}
\item
  Bonilla-Silva E (2022). ``Color-Blind Racism in Pandemic Times.''
  \emph{Sociology of Race and Ethnicity}, \emph{8}(3), 343-354. ISSN
  2332-6492, 2332-6506, doi: 10.1177/2332649220941024 (URL:
  \url{https://doi.org/10.1177/2332649220941024}), \textless URL:
  \url{http://journals.sagepub.com/doi/10.1177/2332649220941024}\textgreater.
  \colorbox{Goldenrod}{\bf{[E-Posting]}}
\end{itemize}

\textbf{Assignments Due:}

\begin{itemize}
\tightlist
\item
  Weekly Perusall Participation
\item
  \textbf{Paper \#3 due on Sunday by 11:59 p.m.}
\item
  \textbf{Quiz \#3 must be completed by Friday 11:59 p.m.}
\end{itemize}

\bigbreak
\hrule

\hypertarget{week-14-1122---1124-fall-break---no-classes-or-assignments---enjoy-your-break}{%
\subsection{WEEK 14, 11/22 - 11/24: FALL BREAK - NO CLASSES OR
ASSIGNMENTS - ENJOY YOUR
BREAK!}\label{week-14-1122---1124-fall-break---no-classes-or-assignments---enjoy-your-break}}

\begin{itemize}
\tightlist
\item
  \textcolor{BurntOrange}{\bf{No required readings or assignments due this week.}}
\end{itemize}

\bigbreak
\hrule

\hypertarget{week-15-1129---1201-feminist-theories-i}{%
\subsection{WEEK 15, 11/29 - 12/01: Feminist Theories,
I}\label{week-15-1129---1201-feminist-theories-i}}

\textbf{Reading Required:}

\begin{itemize}
\tightlist
\item
  Tong R (2009). \emph{Feminist thought: a more comprehensive
  introduction}, 3rd ed edition. Westview Press, Boulder, Colo. ISBN
  978-0-8133-4375-4.
  \colorbox{Goldenrod}{\bf{[E-Posting: Read: Chapters 1, 2, and 3]}}
\end{itemize}

\textbf{Assignments Due:}

\begin{itemize}
\tightlist
\item
  Weekly Perusall Participation
\end{itemize}

\bigbreak
\hrule

\hypertarget{week-16-1206---1208-feminist-theories-ii}{%
\subsection{WEEK 16, 12/06 - 12/08: Feminist Theories
II}\label{week-16-1206---1208-feminist-theories-ii}}

\textbf{Required Readings:}

\begin{itemize}
\item
  Tong R (2009). \emph{Feminist thought: a more comprehensive
  introduction}, 3rd ed edition. Westview Press, Boulder, Colo. ISBN
  978-0-8133-4375-4.
  \colorbox{Goldenrod}{\bf{[E-Posting: Read: Chapter 8 only]}}
\item
  Butler J (1988). ``Performative Acts and Gender Constitution: An Essay
  in Phenomenology and Feminist Theory.'' \emph{Theatre Journal},
  \emph{40}(4), 519. ISSN 01922882, doi: 10.2307/3207893 (URL:
  \url{https://doi.org/10.2307/3207893}), \textless URL:
  \url{https://www.jstor.org/stable/3207893?origin=crossref}\textgreater.
  \colorbox{Goldenrod}{\bf{[E-Posting]}}
\item
  Collins PH (2015). ``Intersectionality's Definitional Dilemmas.''
  \emph{Annual Review of Sociology}, \emph{41}(1), 1-20. ISSN 0360-0572,
  1545-2115, doi: 10.1146/annurev-soc-073014-112142 (URL:
  \url{https://doi.org/10.1146/annurev-soc-073014-112142}),
  \textless URL:
  \url{https://www.annualreviews.org/doi/10.1146/annurev-soc-073014-112142}\textgreater.
  \colorbox{Goldenrod}{\bf{[E-Posting]}}
\end{itemize}

\textbf{Assignments Due:}

\begin{itemize}
\tightlist
\item
  Weekly Perusall Participation
\item
  \textbf{All extra-credit film review/analyses are due on Friday
  December 9 by 11:59 p.m.}
\end{itemize}

\bigbreak
\hrule

\hypertarget{final-examination}{%
\subsection{Final Examination}\label{final-examination}}

\textcolor{ForestGreen}{\bf{There is no formal final exam for this course.}}
Instead, you are required to do the following:

\begin{itemize}
\tightlist
\item
  Complete Quiz \#4 (covering the readings and lectures on theories of
  race and ethnicity, and feminist, queer, and intersectionality
  theories) by \textbf{Friday December 9 11:59 p.m.}
\end{itemize}

AND

\begin{itemize}
\item
  Turn in Analytical Paper \#4 - focusing on either a) theories of race
  and ethnicity; \textbf{OR} b) feminist, queer, intersectionality
  theories. Paper must be turned in by \textbf{Tuesday December 13 11:59
  p.m. in Canvas.}
\item
  \textcolor{BrickRed}{\bf{Optional:}} Turn in up to \textbf{TWO}
  re-written analytical papers. You may resubmit for a higher grade up
  to two (2) of your lowest-scored papers. \textbf{These must be turned
  in by Tuesday December 13 11:59 p.m. in Canvas.}
\end{itemize}

\textbf{\colorbox{LimeGreen}{Syllabus last updated on August 05, 2022}}




\end{document}

\makeatletter
\def\@maketitle{%
  \newpage
%  \null
%  \vskip 2em%
%  \begin{center}%
  \let \footnote \thanks
    {\fontsize{18}{20}\selectfont\raggedright  \setlength{\parindent}{0pt} \@title \par}%
}
%\fi
\makeatother