---
title: 'SOCI 301: Contemporary Social Theory'
date: "Fall 2022"
link-citations: yes
output:
  pdf_document:
    keep_tex: yes
    fig_caption: yes
    number_sections: yes
    latex_engine: pdflatex
    extra_dependencies: xcolor
    template: Syllabus_template.tex
  html_document:
    df_print: paged
geometry: margin=1in
instructor:
- name: Dr. Martín Jacinto
  email: mjacinto@csuchico.edu
  prefered_contact: Blackboard Messaging
  officehours: 10:00 a.m. - 12:00 p.m. Wed
  office: TBD
  correspondence_policy: Respond within 24-48 hours
  instructor:
    
# teachingassistant:
#  - name: Filler
#    email: filler@fill.com
#    officehours: W T
#    office: OfficeNumber
#    sections: '301'

classroom: 'Butte Hall 308'
classhours: 2:00 p.m. - 3:15 p.m.	TuTh
fontfamily: mathpazo
fontsize: 11pt
header-includes: \linespread{1.05}
  -\usepackage{float}
  -\usepackage{booktabs}
  -\usepackage{fontawesome5}
  -\usepackage{color}
  -\usepackage{soul}

---

```{r setup, include=FALSE, ache=F, message=F, warning=F, results="hide"}

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache=TRUE)
knitr::opts_chunk$set(fig.path='figs/')
knitr::opts_chunk$set(cache.path='_cache/')
knitr::opts_chunk$set(warning=F, message=F)

library(timeDate)
library(tibble)
library(dplyr)
library(tidyr)
library(stringr)
library(knitr)
library(RefManageR)
library(knitcitations)
library(rcrossref)
library(bibtex)
library(kableExtra)
library(fontawesome)
library(bibtex)

bib <- read.bib("~/Documents/Github/syllabi/fall_2022/f22_syllabi/Syllabus/general_components/soci301_bib_main.bib")

myopts <- BibOptions(bib.style = "authoryear", style="latex", first.inits=FALSE, max.names = 20)

#This code chunk sets up a table of meeting days for the course.
#You can set days of the week for course meetings (i.e.,. Tuesday and Wednesday).
#Semester start and end dates are selected and then university holidays like spring break are specified.

#Days of the week that the course meets. Must be full day name in quotes.
Days <- c("Tuesday", "Thursday")

#Semester start date for classes as YYYY/M/D.
SemesterStart <- as.Date("2022/8/22")

#Semester end date for classes as YYYY/M/D.
SemesterEnd <- as.Date("2022/12/09")

#Fall break start and stop date.
FallBreak <-
  seq.Date(
    from = as.Date("2022/11/21"),
    to = as.Date("2022/11/25"),
    by = "day"
  )

#Spring break start and stop date.
SpringBreak <-
  seq.Date(
    from = as.Date("2023/03/13"),
    to = as.Date("2023/03/17"),
    by = "day"
  )

#Creates a list of days within the semester.
SemesterDays <-
  seq.Date(from = SemesterStart, to = SemesterEnd, by = "day")

#Add day before Thanksgiving.
DayBeforeThnks<-as.Date(holiday(
    year = getRmetricsOptions("currentYear"),
    Holiday = c("USThanksgivingDay")))-1

#Full list of holidays that there are no classes including breaks.
Holidays <-
  c(as.Date(holiday(
    year = getRmetricsOptions("currentYear"),
    Holiday = c("USLaborDay", "USVeteransDay","USThanksgivingDay", "USMLKingsBirthday")
  )), SpringBreak, FallBreak, DayBeforeThnks)
Holidays

#Create a list of semester days excluding holidays.
SemesterDays <- SemesterDays[!SemesterDays %in% Holidays]

#Make dataframe with all semester days.
ClassDays <- data.frame(index = 1:length(SemesterDays))

#Insert dates.
ClassDays$Date <- SemesterDays

#Insert weekday designation.
ClassDays$Weekday <- weekdays(ClassDays$Date)

#Limit to the class meeting days.
MeetingDays <- ClassDays[ClassDays$Weekday %in% Days, ]

#Create numeric list of weeks.
Week <- cut.Date(MeetingDays$Date, breaks = "week")
levels(Week) <- 1:length(levels(Week))

MeetingDays$Week <- Week
MeetingDays$Class <- 1:nrow(MeetingDays)

#Replace this with c("Lecture topic 1",...,"Lecture topic N") to fill in table.

Lecture_Topic <- 1:nrow(MeetingDays)

MeetingDays <- bind_cols(MeetingDays, Lecture = Lecture_Topic)

#### Grade table ####
Grades <- tribble( ~ Grade,
                   ~ Range, ~Quality,
                   "A",
                   "93 - 100%", "Excellent Work",
                   "A-",
                   "90 - 92%", "Nearly Excellent Work",
                   "B+",
                   "87 - 89%", "Very Good Work", 
                   "B",
                   "83 - 86%", "Good Work",
                   "B-",
                   "80 - 82%", "Mostly Good Work",
                   "C+",
                   "77 - 79%", "Above Average Work",
                   "C",
                   "73 - 76%", "Average Work",
                   "C-",
                   "70 - 72%", "Mostly Average Work",
                   "D+",
                   "67 - 69%", "Below Average Work",
                   "D",
                   "60 - 66%", "Poor Work",
                   "F",
                   "< 60%", "Failing Work")

####Assignment weight table####
Weights <- tribble(~ Item,
                    ~ Weight,
                    "Attendance & Participation",
                    "10 %",
                    "Weekly Perusall Participation & Discussion",
                    "10 %",
                    "Quizzes", 
                    "20 %",
                    "Analytical Response Papers",
                    "60 %",
                    "TOTAL", 
                    "100 %"
                  )


```

```{r indigenous_land_statement, child='general_components/indigenous_land_statement.md'}


```

# Course Description

We all construct and use social theories in our everyday lives. Theory is simply a means of understanding and explaining the social world around us. Social theory allows for seeing patterns, forces, and power relations, encouraging us to make sense of all kinds of social phenomena – ranging from everyday interactions between friends to decades of violent colonization. In this course, we will read theoretical texts every week, and then we will spend time understanding how they have been used to understand specific social phenomena. Theory must be relevant to real life “social facts” for it to survive, and we will work toward bridging the abstract concepts in our readings with the world around us. By the end of the class, you will likely find that some theories are your favorites – more relevant to your everyday life and your own sociological interests than others.

The goal of this course is to deepen your understanding of sociological theories that motivate research and inquiry into our society. In this class, we explore the diversity of major theoretical orientations in sociological thought since the 1950s. Throughout the course of the semester, we will compare core concepts and ideas from these theorists on topics such as social interaction, identity, domination, freedom and perhaps most importantly, power. 

This course requires you to read a lot of social theory, which will be abstract and difficult. I assign primary texts, meaning that they were written by the theorist him/herself. The textbook supplements primary texts by elaborating important notions and concepts across the multipe theoretical perspectives we will cover in the course. While we will contextualize the readings by learning about the theorist’s life, it is important that you learn to read with patience and diligence. I am here to help, as are your classmates. If you are struggling to understand course material on your own, that’s okay! No sociologist learns theory on their own. In this class we situate the readings within their historical and biographical contexts and in conversation with other readings. Through lectures, multiple readings of the material on your own, and class discussions, we will – together – arrive at a deeper understanding of our social world and of the history of sociological thought. 

# Learning Objectives

## Course Learning Objectives
- Gain knowledge about some of the primary theoretical perspectives used within sociology in the 20th and 21st centuries.
- Understand how these perspectives have been shaped by the social context in which they arose. 
- Explore how these perspectives have impacted sociological research and knowledge. 
- Evaluate the strengths and weaknesses of each perspective. 
- Apply the perspectives to our real lives and to the world around us. 

## Sociology Program Student Learning Objectives 
- Demonstrate critical thinking through verbal and written communication. 
- Apply, critically interpret, and synthesize sociological theory. 
- Display an understanding of and appreciation for cultural diversity. 
- Identify processes of social control and how they shape our social institutions and lives. 
- Recognize the relationship between personal agency, social responsibility, and social change (sociological imagination). 
- Display knowledge of the impact of social institutions on everyday lives.

## Course Status
This course is a requirement for the sociology major. It has a prerequisite of SOCI 300, Classical Social Theory, though this prerequisite may be waived with permission of the instructor. *Note that if you take SOCI 301 prior to or concurrent with SOCI 300, you will not be able to repeat SOCI 300 for forgiveness.*

## Important Dates
- Sept. 2nd - Last day to drop without instructor's approval\
- Oct. 24th - Last day to drop and receive financial credit for refund\
- Nov. 10th - Last day to drop or withdraw\
- See the [2022-2023 Academic Calendar](https://www.csuchico.edu/apss/calendar/aca-cal-2022-23.shtml) for more information.

# Course Readings

## Required Textbooks

+ 
    ```{r new, echo = FALSE, results="asis"} 

    bib["dillon_introduction_2020"]

    ``` 

- We will be using the 3rd edition which looks [this](https://www.abebooks.com/Introduction-Sociological-Theory-Theorists-Concepts-Applicability/31208296728/bd?cm_mmc=ggl-_-US_Shopp_Textbook-_-product_id=COM9781119410911USED-_-keyword=&gclid=Cj0KCQjwuO6WBhDLARIsAIdeyDLJvr2N_LKW1qd-49HuMemlLuCRQT4yR3PKWnmeqMDWBDwy9LNFFRUaAlcyEALw_wcB). Previous editions are not permitted. 

## Additional Required Readings

-  Primary texts and other required readings will be available electronically on the Blackboard course page and on Perusall. An \colorbox{Goldenrod}{\bf{“E-Posting”}} notation is made next to each of these readings in the syllabus. These readings will only be available to students enrolled in the course, and are to be used only for educational purposes. 

# Structure and Character of a ChicoFlex Course 

-  **Since this is a [*ChicoFlex* Course](https://www.csuchico.edu/tlp/chicoflex/faq.shtml#whatiscoflex), ALL communications for this course will be conducted via Blackboard Learn**. At Chico State, “this class meets at set days/times in-person (requiring social distancing and face coverings) and is paired with another section taught simultaneously online by the same instructor.” **All times will use Pacific Standard Time (PST).** This means that this class includes campus students who come to a physical class, online students who show up “live,” and online students who watch the archived lectures. Therefore, it is the student’s responsibility to check Blackboard Learn regularly and to check in with the professor or review the Syllabus re: any administrative questions. *Students are required to email the instructor from Blackboard Learn (this will ensure instructor access to emails).*

-  Also, given the fact that we’re still in a global pandemic, the course will proceed fluidly. I want this class to work for all of us and will remain sensitive to the ongoing needs of students while adhering to public health standards and guidelines. 

## Technological Problems: 
- Occasional problems with technology are a common part of the modern university experience. If you have any technical difficulties, you [**should call IT Support Services (ITSS) at 530-898-6000**](https://www.csuchico.edu/itss/). After you call them, if they are not able to resolve the issue, please email me with a description of the problem, the name of the person you spoke to in that office, what they and/or you are doing to resolve the problem, and the expected timeline for its resolution. If you are having trouble with Blackboard Learn during a quiz or other assignment, take a screen shot or photo of the computer screen and the error message you receive and email it to me AND contact ITSS at 530-898-6000. If you experience technical difficulties while submitting an assignment, call ITSS at 1-800-898-6000 and send a copy of the assignment to me via Blackboard Learn. If any of these things happen when ITSS is closed, please follow up with them immediately the next business day. You MUST contact ITSS to resolve the issue if you are asking for any kind of leniency or extension. 

```{r covid-19 policy, child='general_components/COVID_policy.md'}

```

```{r attendance_policy, child='general_components/attendance_policy.md'}

```

# Determination of Final Grade

Table \ref{tab:grade_scale} displays the grading scale that is used to determine a letter grade.

\renewcommand{\arraystretch}{1.5}

```{r Grades_Table, echo=FALSE, results='asis'}

kable(Grades,
      align = c("l", "c", "l"),format="latex",  
      label="grade_scale", caption="Grading Scale") %>%
  kable_styling(font_size=10, latex_options = "hold_position", full_width = F) %>%
  row_spec(0, bold=T) 

```

Table \ref{tab:weight_table} displays how your final grade will be weighed according to the following components:

\renewcommand{\arraystretch}{1.5}

```{r Weights Table, echo=FALSE, results='asis'}

kable(Weights,
      align = c("l", "c"), format="latex", booktabs=T, 
      col.names = c("Item", "% of Final Grade"), 
      label="weight_table", caption="Course Requirements and Grading Policy") %>%
  kable_styling(font_size=10, latex_options = c("hold_position"), full_width = F) %>%
  row_spec(0, bold=T) %>%
  row_spec(6, bold=T, hline_after = T)

```

**Note regarding class workload:** This is a three (3) credit hour class. You should expect to spend two hours outside of class for every one hour in class. This time outside of class will be spent on reading, assignments, and studying. This means you should plan on devoting six hours of outside time per week to this course.     

## Attendance and Class Participation (10% of Final Grade)

The format of this course is an interactive, “live” hybrid lecture and discussion with the objective of collaborative learning and analysis. Participation in class discussion is necessary for your development as a critical scholar and for your understanding of the course material. Participation also includes consistent involvement in online interactive activities. These activities will occur periodically during class throughout the semester. This is a **required** course with difficult reading material and, therefore, it is crucial to establish an informed and critical discourse with each other over the material. Participation includes contributions to class discussions either in class or via class assignments. Participation also includes actively listening, as well as sharing your ideas, criticisms, and frustrations with course material. To ensure active participation, students must come to class having read and taken notes on all material. Furthermore, you are expected to contribute to discussions either in class or via class assignments. Grading of all work is done with the expectation that attendance and participation will be rewarded in the final grade. Also, [see “COVID Policy” section](#covid_policy) above if you are symptomatic and an in-class student. 

In addition to completing all of the assigned reading before each designated day of the week (see reading schedule below and make sure you attend class for the ongoing reading deadlines), you must critically reflect on what is interesting/troubling/useful about what you have read. You are expected to do this work on your own. Be prepared to offer your questions, insights, and critique either via communication with me, writing assignments and/or in conversation with other students. 

**REMEMBER! Attendance is mandatory in all sociology classes (see [Attendance Policy section](#attendance) above). It is also crucial to doing well in this class. In the context of this class, attendance means COMPLETING ALL OF THE ASSIGNMENTS, QUIZZES, INDIVIDUAL WORK, etc.** 

```{r perusall_participation, child='general_components/perusall_participation.md'}

```

## Quizzes (20% of Final Grade; 5% each){#quizzes}

Four quizzes are required in this class. The quizzes will cover theories, ideas, and concepts from the course readings and lectures. **All four required reading quizzes will be posted electronically on Thursday at 4:00 p.m. and must be completed by 11:59 p.m. on Friday.** Each quiz will contain several multiple choice questions based on course readings and lecture material. These quizzes are designed to help you absorb the course readings and lectures, and to provide you with the opportunity to assess your mastery of the theories we are covering in the course. 

**Important Note: Please keep in mind that your lowest quiz score will not be counted when computing final grades. Instead, your highest quiz score will be counted twice in replacement of your lowest quiz score.  All quizzes will be posted on BlackBoard and you will be provided advanced notice.**

## Four (4) Analytical Response Papers (60% of Final Grade; 15% each) {#writing_assignments}

Four papers will be assigned for the semester. The required response papers will answer
either one or two questions posed by the professor based on the course readings and lectures. These assignments will assess knowledge of the course material, critical thinking skills, and writing skills. The papers will require you to be analytical and to reflect deeply on the theoretical works we will cover. Additional instructions about the response papers will be distributed in class during the second week of instruction. **Each paper must be turned in no later than 11:59 p.m. on the day that it is due.** Moreover, please also note that you have options for each paper assignment; this means that for each paper assignment you can choose to write between two sets of theories. Moreover, you have the opportunity to re-write up to **two** of your first three lower-scored analytical response papers for a higher grade. If you decide to rewrite one or two lower-scored papers, these will be due in class on **Tuesday, December 13, 2022 (our “final exam” due date) no later than 11:59 p.m.**

**Due dates for all papers are listed below:**

\renewcommand{\arraystretch}{1.25}

|**Paper**| **Focus**                                 | **Due Date**   |
|---------|-------------------------------------------|----------------|
|Paper #1|Structural Functionalist Theories           |Sunday, Sept. 25|
| | |
|Paper #2|Symbolic Interactionism and the Work of     |Sunday, Oct. 23 |
|        |Erving Goffman; **OR**, Elite, Neo-Marxist, |                |
|        |and Critical Theories                       |                |
| | |
|Paper #3|Post-Structuralist Theory and the Work of   |Sunday, Nov. 20 |
|        |Michel Foucault; **OR**, Pierre Bourdieu and|                |
|        |Theories of Social/ Cultural Reproduction   |                |
|        |and Inequality                              |                |
| | |
|Paper #4|Theories of Race and Ethnicity; **OR**,     |Tuesday, Dec. 13| 
|        |Feminist, Queer, and Intersectionality      |                |
|        |Theories
| | |
|**[Optional]**|Up to **Two** Re-Written Lower-Scored |Tuesday, Dec. 13|
|              |Papers Chosen From The First Three    |                |
|              |Analytical Papers Written             |                |


### Guidelines for papers 
Papers have a word limit, approximately 1000 words (roughly 4 double-spaced pages); must be typed with 12-point font, 1-inch margins, and Times New Roman font (11-point Arial font is also appropriate). Proper grammar and APA citation of sources is expected. **No other format will be accepted.** 

### Tips and tricks for good writing
Use a citation management software to organize your papers and create bibiliographies. My personal preference is [Zotero](https://www.zotero.org/) because it is free, open source, and works across multiple operating systems. For information about other citation management software that is available to CSU Chico students, visit the Meriam Library ["Sample Papers and Citation Tools" page](https://libguides.csuchico.edu/c.php?g=432300&p=2948649). 

Write and then revise. Ask for feedback from peers or wait until you have some distance from your writing and then revise.

Prompt yourself with questions that have short, concrete answers.

## Extra-Credit (Film Reviews & Analyses) [Maximum of 10 Points/5 Points Per Analysis]
Students will have the opportunity to earn extra credit in this course. If you would like to earn up to 10 extra points maximum toward your final course grade, you can write two 1-page (single-spaced) analytical reviews and critiques of two films. The film analyses need to provide a critical sociological review and analysis using one or more of the theories or theorists covered in the course. A list of suggested films/ documentaries will be posted on BlackBoard by the end of the third week of classes along with the guidelines for this assignment. **These extra credit critiques should be concise and well-organized and argued; the film analyses can be submitted at any time during the semester, but no later than Friday December 9 by 11:59 p.m.**

```{r late_work-course_eval, child='general_components/late_work-student_emergencies.md'}

```

```{r contacting_professor, child='general_components/contacting_professor.md'}

```

```{r lectures_slides, child='general_components/lectures_slides.md'}

```

# Creating a Safe and Inclusive Learning Environment 

```{r mandatory_reporting, child='general_components/mandatory_reporting.md'}

```

```{r diversity statements, child='general_components/diversity_statements.md'}

```

```{r mental health, child='general_components/mental_health.md'}

```

```{r other_course_policies, child='general_components/other_course_policies.md'}

```

# University Policies and Campus Resources

```{r Academic Integrity, child='general_components/academic_integrity.md'}

```

```{r Student Services, child='general_components/student_services.md'}

```

```{r Disability Services, child='general_components/disability_services.md'}

```

```{r Food Insecurity, child='general_components/food_insecurity.md'}

```

# Final thoughts

This document is a roadmap for our semester. We learn about social theory together and its applicability towards understanding our environment. Like all your classes, you will get out what you put into this course. Asking for help from one another and your instructors is important, don't be afraid to ask a question about something you don't know or if you want to check your knowledge about something you think you know. Do not wait to ask for help! We are all here to learn; it is not a competition. 

__If this document is updated, a copy will be supplied to you via Black Board and changes will be announced in class.__

\newpage 

\renewcommand{\arraystretch}{1.25}

# Course and Reading Schedule 

The following is a tentative schedule for the Fall 2022 semester. It lists readings and due dates, and **may be subject to change.** Any changes will be announced in class and will be shown in Black Board immediately. Use this information to schedule accordingly. If you miss class, it is your responsibility to find out if any scheduling changes were made in class.

Table \ref{tab:course_schedule} displays the course schedule for the Fall 2022 semester. It lists the days and weeks we will meet for lecture. **We will not meet during Fall Break (Nov. 21-25).**

```{r Schedule, echo=FALSE}

kable(MeetingDays[,c("Date",
                     "Weekday",
                     "Class",
                     "Week",
                     "Lecture")],
  caption = "Course Schedule.", format="latex", booktabs=T, linesep="", 
  label="course_schedule", align = c("l", "l", "c", "c","c")) %>%
  kable_styling(font_size=10, latex_options="hold_position", full_width=F) %>%
  row_spec(0, bold=T)


```

## Tentative Reading and Assignments Schedule

Readings we will cover are listed below. \textcolor{red}{\bf{Note that the professor reserves the right to change the readings and assignment due dates below based on new and developing information about what would best serve my students.}} Changes in the syllabus will be highlighted in \colorbox{Cyan}{\bf{cyan.}} In the event that a reading has not been made available in a way that you can access it on Black Board or Perusall, please email me immediately so the professor may repost the reading/assignment in time for you to complete it before the next class period. You will also be immediately notified when there the due date of an assignment has changed. 

*These are questions you should consider as you complete each reading:* What are the authors’ main objectives/research questions?  What methods, if any, did the author use to explore this question? What are the author’s main conclusions?  How do the readings build upon or challenge other works we have read thus far? Answering these questions on your own will better prepare you for quizzes, writing assignments, and the final project.

# COURSE SCHEDULE
```{r echo=FALSE}

tue <- as.Date("2022-08-23")

# fri <- as.Date("2016-01-08")
advdate <- function(obj, adv) {
 ttue <- obj + 7 * (adv-1)
 tfri <- obj + 2 + 7*(adv-1)
 ttue <- format(ttue, format="%m/%d")
 tfri <- format(tfri, format="%m/%d")
 zadv <- sprintf("%02d", adv)
 tmp <- paste("WEEK ", zadv, sep='',", ", ttue," - ",tfri)
 return(tmp)
}

```

## `r advdate(tue, 1)`: Introduction and Overview of Course

\bigbreak
\hrule

## `r advdate(tue, 2)`: Structural Functionalist Theories, I
    
**Required Readings:**

+
    ```{r week 2a, echo=FALSE, results='asis'}

    bib["dillon_introduction_2020"]
    
    ```
    \textcolor{BrickRed}{\bf{[Read: Chapter 4]}}

+
    ```{r week 2b, echo=FALSE, results='asis'}

    bib["parsons_school_2017"]
    
    ```
    \colorbox{Goldenrod}{\bf{[E-Posting]}}
    
**Assignments Due:**

- Weekly Perusall Participation

\bigbreak
\hrule

## `r advdate(tue, 3)`: Structural Functionalist Theories, II

**Required Readings:**

+
    ```{r week 3a, echo=FALSE, results='asis'}

    bib["merton_social_1938"]
    
    ```
    \colorbox{Goldenrod}{\bf{[E-Posting]}}

+
    ```{r week 3b, echo=FALSE, results='asis'}
    
    bib["davis_principles_1945"]
    ```
    \colorbox{Goldenrod}{\bf{[E-Posting]}}


**Assignments Due:**

- Weekly Perusall Participation

\bigbreak
\hrule

## `r advdate(tue, 4)`: Symbolic Interactionism & the Work of Erving Goffman, I

**Required Readings:**

+
    ```{r week 4a, echo=FALSE, results='asis'}

    bib["dillon_introduction_2020"]
    
    ```
    \textcolor{BrickRed}{\bf{[Read: Chapter 8]}}
    
+
    ```{r week 4b, echo=FALSE, results='asis'}

    bib["rainwater_stigma_2018"]
    
    ```
    \colorbox{Goldenrod}{\bf{[E-Posting]}}


**Assignments Due:**

- Weekly Perusall Participation

\bigbreak
\hrule

## `r advdate(tue, 5)`: The Work of Erving Goffman, II

**Required Readings:**

+
    ```{r week 5, echo=FALSE, results='asis'}
  
    bib["goffman_presentation_1959"]

    ```
    \colorbox{Goldenrod}{\bf{[E-Posting: Read: Introduction and Chapter 1 Only]}}
    
    
**Assignments Due:**

- Weekly Perusall Participation
- **Paper #1 due by Sunday 11:59 p.m.**
- **Quiz #1 must be completed by Friday 11:59 p.m.**

\bigbreak
\hrule

## `r advdate(tue, 6)`: Power Elite Theories

**Required Readings:**

+
    ```{r week 6a, echo=FALSE, results='asis'}

    bib["mills_power_1956"]
    
    ```
    \colorbox{Goldenrod}{\bf{[E-Posting]}}

+
    ```{r week 6b, echo=FALSE, results='asis'}

    bib["molotoch_city_1976"]
    
    ```
    \colorbox{Goldenrod}{\bf{[E-Posting]}}

**Assignments Due:**

- Weekly Perusall Participation

\bigbreak
\hrule

## `r advdate(tue, 7)`: Neo-Marxism and Critical Theories

**Required Readings:**

+
    ```{r week 7a, echo=FALSE, results='asis'}

    bib["gramsci_selections_1971"]
    
    ```
    
    \colorbox{Goldenrod}{\bf{[E-Posting: Read: 238-276 only]}}
    
    
+
    ```{r week 7b, echo=FALSE, results='asis'}

    bib["horkheimer_culture_2017"]
    
    ```
    \colorbox{Goldenrod}{\bf{[E-Posting}}

**Assignments Due:**

- Weekly Perusall Participation

\bigbreak
\hrule

## `r advdate(tue, 8)` Post-Structuralism & the Work of Michel Foucault, I

**Required Readings:**

+
    ```{r week 8a, echo=FALSE, results='asis'}

    bib["dillon_introduction_2020"]
    
    ```
    \textcolor{BrickRed}{\bf{[Read: Chapter 11: 343-352 only]}}

+
    ```{r week 8b, echo=FALSE, results='asis'}
    
    bib["foucault_subject_1982"]
    
    ```
    \colorbox{Goldenrod}{\bf{[E-Posting]}}
    
**Assignments Due:**

- Weekly Perusall Participation

\bigbreak
\hrule

## `r advdate(tue, 9)`: The Work of Michel Foucault, II

**Required Readings:**

+
    ```{r week 9a, echo=FALSE, results='asis'}
    
    bib["foucault_panopticism_2022"]
    
    ```
    \colorbox{Goldenrod}{\bf{[E-Posting]}}

+
    ```{r week 9b, echo=FALSE, results='asis'}

    bib["foucault_history_1978"]
    
    ```
    \colorbox{Goldenrod}{\bf{[E-Posting: Read: 15-73 only]}}

**Assignments Due:**

- Weekly Perusall Participation
- **Paper #2 due by Sunday 11:59 p.m.**
- **Quiz #2 must be completed by Friday 11:59 p.m.**

\bigbreak
\hrule

## `r advdate(tue, 10)`: Theories of Social/Cultural Reproduction & Inequality: The Work of Pierre Bourdieu, I

**Required Readings:**

+
    ```{r week 10a, echo=FALSE, results='asis'}

    bib["dillon_introduction_2020"]
    
    ```
    \textcolor{BrickRed}{\bf{[Read: Chapter 13]}}
    
+
    ```{r week 10b, echo=FALSE, results='asis'}

    bib["bourdieu_structures_1994"]
    
    ```
    \colorbox{Goldenrod}{\bf{[E-Posting]}}

**Assignments Due:**

- Weekly Perusall Participation

\bigbreak
\hrule

## `r advdate(tue, 11)`: The Work of Pierre Bourdieu, II

+
    ```{r week 11a, echo=FALSE, results='asis'}
    
    bib["bourdieu_language_1991"]
    
    ```
    \colorbox{Goldenrod}{\bf{[E-Posting: Read: pp. 43-65 and 163-170]}}

**Assignments Due:**

- Weekly Perusall Participation

\bigbreak
\hrule

## `r advdate(tue, 12)`: Theories of Race & Ethnicity, I


**Required Readings:**

+
    ```{r week 12a, echo=FALSE, results='asis'}

    bib["omi_racial_2020"]

    ```
    \colorbox{Goldenrod}{\bf{[E-Posting]}}

+
    ```{r week 12b, echo=FALSE, results='asis'}

    bib["feagin_rethinking_2013"]
    
    ```
    \colorbox{Goldenrod}{\bf{[E-Posting]}}
   
    
+
    ```{r week 12c, echo=FALSE, results='asis'}

    bib["winant_race_2000"]
    
    ```
    \colorbox{Goldenrod}{\bf{[E-Posting]}}


**Assignments Due:**

- Weekly Perusall Participation

\bigbreak
\hrule

## `r advdate(tue, 13)`: Theories of Race & Ethnicity, II

**Required Readings:**


+
    ```{r week 13a, echo=FALSE, results='asis'}

    bib["lee_americas_2004"]
    
    ```
    \colorbox{Goldenrod}{\bf{[E-Posting]}}

+
    ```{r week 13b, echo=FALSE, results='asis'}
    
    bib["wilson_declining_2011"]
    
    ```
    \colorbox{Goldenrod}{\bf{[E-Posting]}}
    
+
    ```{r week 13c, echo=FALSE, results='asis'}

    bib["bonilla-silva_color-blind_2022"]

    ```
    \colorbox{Goldenrod}{\bf{[E-Posting]}}
    
**Assignments Due:**

- Weekly Perusall Participation
- **Paper #3 due on Sunday by 11:59 p.m.**
- **Quiz #3 must be completed by Friday 11:59 p.m.**

\bigbreak
\hrule  

## `r advdate(tue, 14)`: FALL BREAK - NO CLASSES - ENJOY YOUR BREAK!

- \textcolor{BurntOrange}{\bf{No required readings or assignments due this week.}}

\bigbreak
\hrule

## `r advdate(tue, 15)`: Feminist Theories, I


**Reading Required:**

+
    ```{r week 15a, echo=FALSE, results='asis'}

    bib["tong_feminist_2009"]
    
    ```
    \colorbox{Goldenrod}{\bf{[E-Posting: Read: Chapters 1, 2, and 3]}}
    

**Assignments Due:**

- Weekly Perusall Participation

\bigbreak
\hrule

## `r advdate(tue, 16)`: Feminist Theories II

**Required Readings:**

+
    ```{r week 16a, echo=FALSE, results='asis'}

    bib["tong_feminist_2009"]
    
    ```
    \colorbox{Goldenrod}{\bf{[E-Posting: Read: Chapter 8 only]}}

+
    ```{r week 16b, echo=FALSE, results='asis'}
    
    bib["butler_performative_1988"]

    ```
    \colorbox{Goldenrod}{\bf{[E-Posting]}}

+
    ```{r week 16c, echo=FALSE, results='asis'}

    bib["collins_intersectionalitys_2015"]
    
    ```
    \colorbox{Goldenrod}{\bf{[E-Posting]}}

**Assignments Due:**

- Weekly Perusall Participation
- **All extra-credit film review/analyses are due on Friday December 9 by 11:59 p.m.**

\bigbreak
\hrule

## Final Examination

\textcolor{ForestGreen}{\bf{There is no formal final exam for this course.}} Instead, you are required to do the following:

- Complete Quiz #4 (covering the readings and lectures on theories of race
and ethnicity, and feminist, queer, and intersectionality theories) by **Friday December 9 11:59 p.m.**

AND

- Turn in Analytical Paper #4 - focusing on either a) theories of race and ethnicity; **OR** b) feminist, queer, intersectionality theories. Paper must be turned in by **Tuesday December 13 11:59 p.m. in Blackboard.**

- \textcolor{BrickRed}{\bf{Optional:}} Turn in up to **TWO** re-written analytical papers. You may resubmit for a higher grade up to two (2) of your lowest-scored papers. **These must be turned in by Tuesday December 13 11:59 p.m. in Blackboard.**


