\documentclass[11pt,]{article}
\usepackage[margin=1in]{geometry}
\newcommand*{\authorfont}{\fontfamily{phv}\selectfont}
\usepackage[]{mathpazo}
\usepackage{multicol}
\usepackage{abstract}
\renewcommand{\abstractname}{}    % clear the title
\renewcommand{\absnamepos}{empty} % originally center
\newcommand{\blankline}{\quad\pagebreak[2]}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}} 
\usepackage{longtable,booktabs}
      
\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}

\titleformat*{\subsubsection}{\normalsize\itshape}

\usepackage{titling}
\setlength{\droptitle}{-.15cm}

%\setlength{\parindent}{0pt}
%\setlength{\parskip}{6pt plus 2pt minus 1pt}
%\setlength{\emergencystretch}{3em}  % prevent overfull lines 

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{lastpage}
\renewcommand{\headrulewidth}{0.3pt}
\renewcommand{\footrulewidth}{0.0pt} 
\lhead{}
\chead{}
\rhead{\footnotesize SOCI 301: Contemporary Social Theory -- Fall 2022}
\lfoot{}
\cfoot{\small \thepage /\pageref*{LastPage}}
\rfoot{}

\fancypagestyle{firststyle}
{
\renewcommand{\headrulewidth}{0pt}%
   \fancyhf{}
   \fancyfoot[C]{\small \thepage/\pageref*{LastPage}}
}

%\def\labelitemi{--}
%\usepackage{enumitem}
%\setitemize[0]{leftmargin=25pt}
%\setenumerate[0]{leftmargin=25pt}




\makeatletter
\@ifpackageloaded{hyperref}{}{%
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
}
\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
             pdfkeywords = {},  
            pdftitle={SOCI 301: Contemporary Social Theory},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls


\setcounter{secnumdepth}{0}

\usepackage{longtable}




\usepackage{setspace}

\title{SOCI 301: Contemporary Social Theory}
\date{Fall 2022}


\begin{document}  

		\maketitle
		
	
		\thispagestyle{firststyle}

%	\thispagestyle{empty}
\textbf{\underline{Instructor}}
\begin{multicols}{2}

  \textbf{Dr.~Martín Jacinto}\\
  Email: \href{mailto:mjacinto@csuchico.edu}{\nolinkurl{mjacinto@csuchico.edu}}\\
  Preferred contact: Blackboard Messaging\\
  Office Hours: 10:00 a.m. - 12:00 p.m. Wed\\
  Office: TBD\\
  Correspondence policy: Respond within 24-48 hours\\
    \columnbreak
    
  \end{multicols}
	
\noindent \begin{tabular*}{\textwidth}{ @{\extracolsep{\fill}} lr @{\extracolsep{\fill}}}
\textbf{\underline{Class information}}\\
  Classroom: Butte Hall 308\\
  Class Hours: 2:00 pm - 3:15 pm TuTh\\
    \\
	\end{tabular*}\\


\vspace{2mm}


\hypertarget{course-description}{%
\section{Course Description}\label{course-description}}

We all construct and use social theories in our everyday lives. Theory
is simply a means of understanding and explaining the social world
around us. Social theory allows for seeing patterns, forces, and power
relations, encouraging us to make sense of all kinds of social phenomena
-- ranging from everyday interactions between friends to decades of
violent colonization. In this course, we will read theoretical texts
every week, and then we will spend time understanding how they have been
used to understand specific social phenomena. Theory must be relevant to
real life ``social facts'' for it to survive, and we will work toward
bridging the abstract concepts in our readings with the world around us.
By the end of the class, you will likely find that some theories are
your favorites -- more relevant to your everyday life and your own
sociological interests than others.

The goal of this course is to deepen your understanding of sociological
theories that motivate research and inquiry into our society. In this
class, we explore the diversity of major theoretical orientations in
sociological thought since the 1950s. Throughout the course of the
semester, we will compare core concepts and ideas from these theorists
on topics such as social interaction, identity, domination, freedom and
perhaps most importantly, power.

This course requires you to read a lot of social theory, which will be
abstract and difficult. I assign primary texts, meaning that they were
written by the theorist him/herself. The textbook supplements primary
texts by elaborating important notions and concepts across the multipe
theoretical perspectives we will cover in the course. While we will
contextualize the readings by learning about the theorist's life, it is
important that you learn to read with patience and diligence. I am here
to help, as are your classmates. If you are struggling to understand
course material on your own, that's okay! No sociologist learns theory
on their own. In this class we situate the readings within their
historical and biographical contexts and in conversation with other
readings. Through lectures, multiple readings of the material on your
own, and class discussions, we will -- together -- arrive at a deeper
understanding of our social world and of the history of sociological
thought.

\hypertarget{learning-objectives}{%
\section{Learning Objectives}\label{learning-objectives}}

\hypertarget{course-learning-objectives}{%
\subsection{Course Learning
Objectives}\label{course-learning-objectives}}

\begin{itemize}
\tightlist
\item
  Gain knowledge about some of the primary theoretical perspectives used
  within sociology in the 20th and 21st centuries.
\item
  Understand how these perspectives have been shaped by the social
  context in which they arose.
\item
  Explore how these perspectives have impacted sociological research and
  knowledge.
\item
  Evaluate the strengths and weaknesses of each perspective.
\item
  Apply the perspectives to our real lives and to the world around us.
\end{itemize}

\hypertarget{sociology-program-student-learning-objectives}{%
\subsection{Sociology Program Student Learning
Objectives}\label{sociology-program-student-learning-objectives}}

\begin{itemize}
\tightlist
\item
  Demonstrate critical thinking through verbal and written
  communication.
\item
  Apply, critically interpret, and synthesize sociological theory.
\item
  Display an understanding of and appreciation for cultural diversity.
\item
  Identify processes of social control and how they shape our social
  institutions and lives.
\item
  Recognize the relationship between personal agency, social
  responsibility, and social change (sociological imagination).
\item
  Display knowledge of the impact of social institutions on everyday
  lives.
\end{itemize}

\hypertarget{course-status}{%
\subsection{Course Status}\label{course-status}}

This course is a requirement for the sociology major.It has a
prerequisite of SOCI 300, Classical Social Theory, though this
prerequisite may be waived with permission of the instructor. \emph{Note
that if you take SOCI 301 prior to or concurrent with SOCI 300, you will
not be able to repeat SOCI 300 for forgiveness.}

\hypertarget{important-dates}{%
\subsection{Important Dates}\label{important-dates}}

Sept.~2nd - Last day to drop without instructor's approval\\
Oct.~24th - Last day to drop and receive financial credit for refund\\
Nov.~10th - Last day to drop or withdraw\\
See the
\href{https://www.csuchico.edu/apss/calendar/aca-cal-2022-23.shtml}{2022-2023
Academic Calendar} for more information.

\hypertarget{course-readings}{%
\section{Course Readings}\label{course-readings}}

\hypertarget{required-textbooks}{%
\subsection{Required Textbooks}\label{required-textbooks}}

Dillon, Michele (2010).
\emph{Introduction to Sociological Theory: Theorists, Concepts, and their Applicability to the Twenty-First Century, 3rd Edition}.
Hoboken, NJ: Wiley \& Sons Ltd. ISBN: 9781119410911.

\begin{itemize}
\tightlist
\item
  We will be using the 3rd edition which looks
  \href{https://www.abebooks.com/Introduction-Sociological-Theory-Theorists-Concepts-Applicability/31208296728/bd?cm_mmc=ggl-_-US_Shopp_Textbook-_-product_id=COM9781119410911USED-_-keyword=\&gclid=Cj0KCQjwuO6WBhDLARIsAIdeyDLJvr2N_LKW1qd-49HuMemlLuCRQT4yR3PKWnmeqMDWBDwy9LNFFRUaAlcyEALw_wcB}{this}.
  Previous editions are not permitted.
\end{itemize}

\hypertarget{additional-required-readings}{%
\subsection{Additional Required
Readings}\label{additional-required-readings}}

\begin{itemize}
\tightlist
\item
  Primary texts and other required readings will be available
  electronically on the Blackboard Learn course page and on Perusall.
\end{itemize}

\hypertarget{structure-and-character-of-a-chicoflex-course}{%
\section{Structure and Character of a ChicoFlex
Course}\label{structure-and-character-of-a-chicoflex-course}}

\begin{itemize}
\item
  \textbf{Since this is a
  \href{https://www.csuchico.edu/tlp/chicoflex/faq.shtml\#whatiscoflex}{\emph{ChicoFlex}
  Course}, ALL communications for this course will be conducted via
  Blackboard Learn}. At Chico State, ``this class meets at set
  days/times in-person (requiring social distancing and face coverings)
  and is paired with another section taught simultaneously online by the
  same instructor.'' This means that this class includes campus students
  who come to a physical class, online students who show up ``live,''
  and online students who watch the archived lectures. Therefore, it is
  the student's responsibility to check Blackboard Learn regularly and
  to check in with the professor or review the Syllabus re: any
  administrative questions. \emph{Students are required to email the
  instructor from Blackboard Learn (this will ensure instructor access
  to emails).}
\item
  Also, given the fact that we're still in a global pandemic, the course
  will proceed fluidly. I want this class to work for all of us and will
  remain sensitive to the ongoing needs of students while adhering to
  public health standards and guidelines.
\end{itemize}

\hypertarget{technological-problems}{%
\subsection{Technological Problems:}\label{technological-problems}}

\begin{itemize}
\tightlist
\item
  Occasional problems with technology are a common part of the modern
  university experience. If you have any technical difficulties, you
  \textbf{should call the university technology folks at 530-898-6000}.
  After you call them, if they are not able to resolve the issue, please
  email me with a description of the problem, the name of the person you
  spoke to in that office, what they and/or you are doing to resolve the
  problem, and the expected timeline for its resolution. If you are
  having trouble with Blackboard Learn during a quiz or other
  assignment, take a screen shot or photo of the computer screen and the
  error message you receive and email it to me AND contact ITSS at
  530-898-6000. If you experience technical difficulties while
  submitting an assignment, call ITSS at 1-800-898-6000 and send a copy
  of the assignment to me via Blackboard Learn. If any of these things
  happen when ITSS is closed, please follow up with them immediately the
  next business day. You MUST contact ITSS to resolve the issue if you
  are asking for any kind of leniency or extension.
\end{itemize}

\hypertarget{covid-policy}{%
\section{COVID policy}\label{covid-policy}}

\href{https://calstate.policystat.com/policy/11030468/latest/}{Per the
California State University Chancellor's Office policy, the Covid-19
vaccine and booster is required for students, faculty and staff, unless
you obtain an exemption from the university}. Currently, Chico State is
requiring everyone on campus to wear an approved face covering in all
indoor campus spaces. Accordingly, all students are required to wear an
appropriate face mask covering the nose and mouth in order to
participate in this course. Policies and requirements regarding COVID-19
are subject to change pursuant to campus, local, state and/or federal
guidelines.

Please note that dishonesty relating to the vaccination policy and/or
your failure to comply with any other COVID-19 related safety policy or
mandate, including the face covering requirement, may result in
disciplinary action against you through the office of Student Conduct,
Rights and Responsibilities, which can include suspension or expulsion
from the California State University system.

Individuals unable to wear a face covering due to a medical condition
should contact the Accessibility Resource Center by phone at (530)
898-5959 or by email at
\href{mailto:arcdept@csuchico.edu}{\nolinkurl{arcdept@csuchico.edu}}.

COVID policy re: attendance: Attendance in this class is mandatory; if
you do not attend class, you will not pass. If, however, you are a
campus student attending physical class and you are symptomatic, please
contact me (via email), do not attend the in-person class, and contact
the COVID hotline at \textbf{530-898-2222} for additional direction.
Also, make sure you keep me updated as you learn more about your health
status.

\hypertarget{attendance}{%
\section{Attendance Policy}\label{attendance}}

\textbf{Attendance and Ongoing Participation in Sociology Courses is
mandatory in all sociology classes and is essential to your success in
this course.} Only documented emergencies will constitute excused
absences or assignments. Documentation will only be accepted within one
week of your return to class. Please do not contact me about
non-emergency absences. You are allowed up to three (3) unexcused
absences and anything more than that will affect your final grade. If
you expect to miss class because of a religious observance, you will
need to notify me beforehand. Finally, if you miss class, it is your
responsibility to catch up.

\hypertarget{dropped-from-the-course}{%
\subsection{Dropped From The Course}\label{dropped-from-the-course}}

In accordance with the college drop policy, students who do not access
the class web site or submit the designated ``first assignments'' by the
due date may be dropped as a no show. Students who fail to turn in the
weekly assignments and/or participate in the discussion boards will be
considered ``absent'' and may be dropped from the class for ``excessive
absence.'' Students are responsible for officially dropping the class or
they will receive a letter grade based on their performance.

\begin{itemize}
\item
  \textbf{No Show Drop:} You must complete a designated discussion post,
  quiz, or practice activity by Tuesday of the first week of class or
  you may be dropped as a no-show. Students who do not complete any work
  in the first week will be dropped.
\item
  \textbf{Excessive Absence Drop:} If more than two consecutive weeks of
  non-participation is observed by the instructor the student may be
  dropped. If you do not participate in each week's discussion board and
  complete at least one quiz or practice activity, you will be
  considered ``non-participating'' and subject to being dropped from the
  course.
\end{itemize}

\hypertarget{determination-of-final-grade}{%
\section{Determination of Final
Grade}\label{determination-of-final-grade}}

At the university level, it is a great achievement to earn the grade of
A. It is especially worthwhile to earn an A as an overall final course
grade. The grade of A is the highest recognition and commendation there
is at the university classroom level. Its use in this course will be in
that spirit, consistent with the traditional meaning of ``excellence.''
At the same time, I wish to make it perfectly clear that \textbf{your
grades in this class are NOT an evaluation of you as a person.} For
people on both ends of the grading scale, it is sometimes necessary to
remember that you are more than just your grades.

Table \ref{tab:grade_scale} displays the grading scale that is used to
determine a letter grade.

\renewcommand{\arraystretch}{1.5}

\begin{table}[!h]

\caption{\label{tab:grade_scale}Grading Scale}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{l|c|l}
\hline
\textbf{Grade} & \textbf{Range} & \textbf{Quality}\\
\hline
A & 93 - 100\% & Excellent Work\\
\hline
A- & 90 - 92\% & Nearly Excellent Work\\
\hline
B+ & 87 - 89\% & Very Good Work\\
\hline
B & 83 - 86\% & Good Work\\
\hline
B- & 80 - 82\% & Mostly Good Work\\
\hline
C+ & 77 - 79\% & Above Average Work\\
\hline
C & 73 - 76\% & Average Work\\
\hline
C- & 70 - 72\% & Mostly Average Work\\
\hline
D+ & 67 - 69\% & Below Average Work\\
\hline
D & 60 - 66\% & Poor Work\\
\hline
F & < 60\% & Failing Work\\
\hline
\end{tabular}
\end{table}

Table \ref{tab:weight_table} displays how your final grade will be
weighed according to the following components:

\renewcommand{\arraystretch}{1.5}

\begin{table}[!h]

\caption{\label{tab:weight_table}Course Requirements and Grading Policy}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lc}
\toprule
\textbf{Item} & \textbf{\% of Final Grade}\\
\midrule
Attendance \& Participation & 15 \%\\
Weekly Perusall Participation \& Discussion & 15 \%\\
Quizzes & 15 \%\\
Three (3) Writing Assignments & 25 \%\\
Final Paper & 30 \%\\
\addlinespace
\textbf{TOTAL} & \textbf{100 \%}\\
\midrule
\bottomrule
\end{tabular}
\end{table}

\textbf{Note regarding class workload:} This is a three (3) credit hour
class. You should expect to spend two hours outside of class for every
one hour in class. This time outside of class will be spent on reading,
assignments, and studying. This means you should plan on devoting six
hours of outside time per week to this course.

\newpage

\hypertarget{attendance-and-class-participation-15-of-final-grade}{%
\subsection{Attendance and Class Participation (15\% of Final
Grade)}\label{attendance-and-class-participation-15-of-final-grade}}

The format of this course is an interactive, ``live'' hybrid lecture and
discussion with the objective of collaborative learning and analysis.
Participation in class discussion is necessary for your development as a
critical scholar and for your understanding of the course material. This
is a \textbf{required} course with difficult reading material and,
therefore, it is crucial to establish an informed and critical discourse
with each other over the material. Participation includes contributions
to class discussions either in class or via class assignments.
Participation also includes actively listening, as well as sharing your
ideas, criticisms, and frustrations with course material. To ensure
active participation, students must come to class having read and taken
notes on all material. Furthermore, you are expected to contribute to
discussions either in class or via class assignments. Grading of all
work is done with the expectation that attendance and participation will
be rewarded in the final grade. Also, see ``COVID Directions'' (above)
if you are symptomatic and an in-class student.

In addition to completing all of the assigned reading before each
designated day of the week (see reading schedule below and make sure you
attend class for the ongoing reading deadlines), you must critically
reflect on what is interesting/troubling/useful about what you have
read. You are expected to do this work on your own. Be prepared to offer
your questions, insights, and critique either via communication with me,
writing assignments and/or in conversation with other students.

\emph{These are questions you should consider as you complete each
reading:} What are the authors' main objectives/research questions? What
methods, if any, did the author use to explore this question? What are
the author's main conclusions? How do the readings build upon or
challenge other works we have read thus far? Answering these questions
on your own will better prepare you for quizzes, writing assignments,
and the final project.

\textbf{REMEMBER! Attendance is mandatory in all sociology classes (see
\protect\hyperlink{attendance}{Attendance Policy section} above). It is
also crucial to doing well in this class. In the context of this class,
attendance means COMPLETING ALL OF THE ASSIGNMENTS, QUIZZES, INDIVIDUAL
WORK, etc.} \emph{I usually have a very strict attendance policy.}

\hypertarget{weekly-perusall-participation-15-of-final-grade}{%
\subsection{Weekly Perusall Participation (15\% of Final
Grade)}\label{weekly-perusall-participation-15-of-final-grade}}

For reading we will use
\href{https://support.perusall.com/hc/en-us}{Perusall}, a social
annotation tool that allows students and their instructors to
collaboratively markup .pdf documents. Instead of only reading a
document and discussing it, Perusall brings discussion to text.

To start, register for a free Perusall account and enter the course
code: {[}Insert Code Here{]}

At the beginning of the quarter, you will be assigned to groups in
Perusall, each comprised of around 10-12 students. After week 2, you
will be randomly placed into these groups and participate in
asynchronous group reading and discussion, covering any major theme(s)s
or issue(s) from the reading and lecture.

You will each read and discuss within your group forum. This means that
you must not only do the reading and annotate on your own, but you must
ask and respond to one or more questions within your group that are
related to that week's readings assignment(s) and lecture. Thus, you
must interact in your group forum with at least two (2) of your
groupmate's posts. Your contribution and annotations will be graded on a
scale of 1 -- 3, with higher scores indicating higher quality
annotations and responses. Your response to two or more groupmate's
annotations and questions (due by 8:00 PM (Pacific Standard Time) on
Friday of that week). \textbf{Discussion posts and annotations will be
given credit only if they are substantive and follow all instructions.}

For reading assignments in Perusall, you will be evaluated based on the
following four criteria:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Quality: The more thoughtful the responses, the higher the score.
\item
  Quantity: Each student must submit at least seven (7) annotations in
  each reading document. I will then compute overall grade based on
  highest quality annotations.
\item
  Timeliness: You must complete the reading assignment by Friday 8:00PM.
\item
  Distribution: Are annotations made throughout the document? If most
  annotations are made in a single area, it indicates the student did
  not engage with the entire document. If annotations are distributed
  throughout the entire document, it indicates the student did engage
  with the reading in entirety.
\item
  Asking/Answering Questions: Ask and respond to each other's comments
  and questions in their group forums.
\end{enumerate}

? Common question! What if I don't have any questions or comments?
Elaborate on a specific topic, connect to personal experience or
perspective, extension to another topic or perspective, paraphrase part
of the text.

\hypertarget{quizzes-15-of-final-grade}{%
\subsection{Quizzes (15\% of Final
Grade)}\label{quizzes-15-of-final-grade}}

Throughout the course, I will ask students to synthesize, analyze,
and/or apply contemporary social theories and readings from the previous
day(s) or week(s) via a fairly short, intense quiz (typically, 3-10
multiple-choice and/or short answer questions). The quiz closes after
the posted due date. In order to avoid missing a quiz and any
announcements I have, make sure you check Blackboard Learn every single
day of the week. The quiz closes after the posted due date. In order to
avoid missing a quiz and any announcements I have, make sure you check
Blackboard Learn every single day of the week. \emph{No quiz will be
assigned the week a writing assignment is due.}

\hypertarget{writing_assignments}{%
\subsection{Three (3) Writing Assignments (25\% of Final
Grade)}\label{writing_assignments}}

Students will complete at least 3 small writing assignments throughout
the course. These assignments will assess knowledge of the course
material, critical thinking skills, and writing skills. Guidelines for
the papers will be given out at least two weeks in advance. Papers will
have a word limit, approx. 750 words (roughly 3 double-spaced pages),
typed, 12-point font, 1-inch margins, Times New Roman (11-point Arial
font is also appropriate). Proper grammar and APA citation of sources is
expected. \textbf{No other format will be accepted.} Late papers will be
deducted 20\% of its overall grade each day that it is overdue.

\hypertarget{final-paper-30-of-final-grade}{%
\subsection{Final Paper (30\% of Final
Grade)}\label{final-paper-30-of-final-grade}}

Building upon the ideas you developed in the writing assignments and
other assignments, you will write a \textbf{final 1,000 word (roughly 4
double-spaced pages) paper for this class.} In this paper, you will
apply, expand, or challenge theories we covered in class. In this paper,
you will apply, expand, or challenge theory. If you apply theory, you
will use one of the main theoretical frameworks we covered in the course
to sociologically analyze a cultural artifact (examples: documentary
film(s), popular film(s), popular music, magazines, novels, etc.; speak
with me about the appropriate cultural artifact). If you expand theory,
you will make an argument for the expansion of any theory we have
covered in the course, thus making that theory better, more
contemporary, and/or more inclusive. If you challenge theory, you will
accurately describe the theory you are challenging, make an argument for
how and why you are challenging the theory, and perhaps offer a new
theory that might replace the theory you are challenging. Before you
begin your paper, speak with me about your main ideas and outline for
the paper. I will post a detailed rubric and example of an excellent
Final Paper on Blackboard about a month before the due date.

\hypertarget{tips-and-tricks-for-good-writing}{%
\subsubsection{Tips and tricks for good
writing}\label{tips-and-tricks-for-good-writing}}

Use a citation management software to organize your papers and create
bibiliographies. My personal preference is
\href{https://www.zotero.org/}{Zotero} because it is free, open source,
and works across multiple operating systems. For information about other
citation management software that is available to CSU Chico students,
visit the Meriam Library
\href{https://libguides.csuchico.edu/c.php?g=432300\&p=2948649}{``Sample
Papers and Citation Tools'' page}.

Write and then revise. Ask for feedback from peers or wait until you
have some distance from your writing and then revise.

Prompt yourself with questions that have short, concrete answers.

\hypertarget{late-work}{%
\subsection{Late Work}\label{late-work}}

Participation in discussions (Perusall or otherwise) must be on time so
that others can respond to your posts. Thus, \textbf{discussion posts
will not be accepted late for any reason (no matter how good you think
your reason is).} Quizzes, practice activities, and essay assignments
are a bit different. If you must submit one of these assignments late,
please contact me right away. The longer you wait, the less likely I am
to accept the assignment. I reserve the right to refuse any late work,
but keeping the lines of communication open is your best bet if you fall
a little behind on an assignment.

\hypertarget{getting-help-and-communicating-with-your-professor}{%
\section{Getting Help And Communicating With Your
Professor}\label{getting-help-and-communicating-with-your-professor}}

Remember, your professor is here to help you gain a rich understanding
of the material. So, it is important to be connected to your instructor
and seek help whenever you need it. However, it is primarily your
responsibility to seek help when you need it. Use the following methods
to get in touch and/or ask questions.

\hypertarget{communication-policy}{%
\subsection{Communication policy}\label{communication-policy}}

When contacting your about the course, please send message through
``Message Your Professor'' in BBLearn. I check messages three times per
day, Monday thru Friday, between 9:00 AM and 6:00 PM. Please allow up to
24-48 hours for a response during the week. If you contact on the
weekend, expect a reply the following Monday.

\begin{itemize}
\item
  Requesting help: If you miss a class meeting, you should\ldots{}

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \tightlist
  \item
    First, look on the course website for material you missed.
  \item
    Second, if you need help understanding the material, you should
    contact your classmate via Beach. Board (direct email or discussion
    board).
  \item
    Third, if you still find it difficult, find some time to chat with
    me during office hours
  \end{enumerate}
\item
  Requesting a 1-on-1, non-office-hour Zoom meeting:

  \begin{quote}
  If, after you've looked over the material yourself and reached out to
  classmates, you still need help but cannot attend office hours, you
  may email me to request a virtual Zoom meeting. For non-office-hour
  zoom meetings, I require at least a minimum of one-week's notice.
  \end{quote}
\item
  On-line communication

  \begin{itemize}
  \tightlist
  \item
    I require that all communication be done in a respectful, courteous,
    and professional manner. When in doubt, always err in these
    directions; for example, aim for being slightly more courteous than
    you may think you need to be. Nobody will object to an extra
    ``please'' or ``thank you.'' Always take a few minutes to read what
    you have written before posting a comment or sending an email --
    pause and think -- could what you have written be construed as
    disrespectful, impolite, or snappy? When in doubt, re-think your
    words and tone, and re-calibrate your message. We may not always
    agree but disagreeing while simultaneously showing respect and
    courtesy toward someone is a skill that will serve you well
    throughout your life and in many contexts. Always make criticism
    constructive and not personal. If you disagree with someone, they
    should not feel personally attacked. Keep the ideas separate from
    the person. I will always keep these principles in mind when
    communicating with you -- please do the same toward me and your
    fellow students.
  \end{itemize}
\end{itemize}

\textbf{I reserve the right to penalize individuals who do not
demonstrate these basic principles in their communications.}

\#Other Course Policies

\begin{itemize}
\item
  Unless you have a documented emergency, there will be no substitutions
  for assignments, quizzes, or papers. A missed assignment, quiz, or
  paper will result in a zero. Incomplete grades (or an ``I'' grade) are
  rare, and will be given at the discretion of the professor.
\item
  ``Pet Peeves'':

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \tightlist
  \item
    Asking to be excused from rules that all classmates are following.
  \item
    Inappropriate or disruptive behavior will not be tolerated. If this
    behavior persists, the student will be reported to the Dean's
    Office.
  \end{enumerate}
\end{itemize}

\newpage

\hypertarget{campus-resources}{%
\section{Campus resources}\label{campus-resources}}

\hypertarget{writing-center}{%
\subsection{Writing center}\label{writing-center}}

Over the course of this semester, seek help at the Writing Center if you
would like additional guidance and critique. You can access the Writing
Center at
\href{https://www.southalabama.edu/departments/academicsuccess/cae/how.it.works.html}{at
their website}. During graduate school, I found workshops and writing
groups at the Writing Center on campus to be helpful in building my
motivation and teaching me new strategies for writing efficiently.

\hypertarget{disabilities}{%
\subsection{Disabilities}\label{disabilities}}

In accordance with the Americans with Disabilities Act, students with
bona fide disabilities will be afforded reasonable accommodations. The
Office of Special Student Services (OSSS) will certify a disability and
advise faculty members of reasonable accommodations. If you have a
specific disability that qualifies you for academic accommodations,
please notify the instructor/professor and provide certification from
the Office of Special Student Services. OSSS is located at 5828 Old
Shell Road at Jaguar Drive, (251-460-7212).

\hypertarget{food-insecurity}{%
\subsection{Food insecurity}\label{food-insecurity}}

If you are subject to food insecurity, JagPantry provides a food for
students needing assistance. More information can be found
\href{https://www.southalabama.edu/departments/sga/foodpantry.html}{on
their website}

\hypertarget{mental-health}{%
\subsection{Mental health}\label{mental-health}}

Being a university student is stressful and can negatively impact mental
health. The University Counseling and Testing Center provides
confidential, free counseling and crisis intervention services to
eligible USA students and consultation and outreach services to members
of the USA community. More information can be found
\href{https://www.southalabama.edu/departments/counseling/}{at their
website}.

\hypertarget{final-thoughts}{%
\section{Final thoughts}\label{final-thoughts}}

This document is a roadmap for our semester. We learn about the Earth
together and our individual experiences shape how we interpret and value
data. Like all your classes, you will get out what you put into this
course. Asking for help from one another and your instructors is
important, don't be afraid to ask a question about something you don't
know or if you want to check your knowledge about something you think
you know.

\textbf{If this document is updated, a copy will be supplied to you via
Blackboard and changes will be announced in class.}

\newpage

\renewcommand{\arraystretch}{1.25}

\begin{longtable}[]{@{}lccl@{}}
\caption{Course Schedule.}\tabularnewline
\toprule
Date & Class & Week & Lecture \\
\midrule
\endfirsthead
\toprule
Date & Class & Week & Lecture \\
\midrule
\endhead
2022-08-23 & 1 & 1 & 1 \\
2022-08-25 & 2 & 1 & 2 \\
2022-08-30 & 3 & 2 & 3 \\
2022-09-01 & 4 & 2 & 4 \\
2022-09-06 & 5 & 3 & 5 \\
2022-09-08 & 6 & 3 & 6 \\
2022-09-13 & 7 & 4 & 7 \\
2022-09-15 & 8 & 4 & 8 \\
2022-09-20 & 9 & 5 & 9 \\
2022-09-22 & 10 & 5 & 10 \\
2022-09-27 & 11 & 6 & 11 \\
2022-09-29 & 12 & 6 & 12 \\
2022-10-04 & 13 & 7 & 13 \\
2022-10-06 & 14 & 7 & 14 \\
2022-10-11 & 15 & 8 & 15 \\
2022-10-13 & 16 & 8 & 16 \\
2022-10-18 & 17 & 9 & 17 \\
2022-10-20 & 18 & 9 & 18 \\
2022-10-25 & 19 & 10 & 19 \\
2022-10-27 & 20 & 10 & 20 \\
2022-11-01 & 21 & 11 & 21 \\
2022-11-03 & 22 & 11 & 22 \\
2022-11-08 & 23 & 12 & 23 \\
2022-11-10 & 24 & 12 & 24 \\
2022-11-15 & 25 & 13 & 25 \\
2022-11-17 & 26 & 13 & 26 \\
2022-11-29 & 27 & 15 & 27 \\
2022-12-01 & 28 & 15 & 28 \\
2022-12-06 & 29 & 16 & 29 \\
2022-12-08 & 30 & 16 & 30 \\
\bottomrule
\end{longtable}




\end{document}

\makeatletter
\def\@maketitle{%
  \newpage
%  \null
%  \vskip 2em%
%  \begin{center}%
  \let \footnote \thanks
    {\fontsize{18}{20}\selectfont\raggedright  \setlength{\parindent}{0pt} \@title \par}%
}
%\fi
\makeatother