---
title: 'SOCI 301: Contemporary Social Theory'
date: "Fall 2022"
link-citations: yes
output:
  pdf_document:
    keep_tex: yes
    fig_caption: yes
    number_sections: yes
    latex_engine: pdflatex
    template: Syllabus_template.tex
  html_document:
    df_print: paged
geometry: margin=1in
instructor:
- name: Dr. Martín Jacinto
  email: mjacinto@csuchico.edu
  prefered_contact: Blackboard Messaging
  officehours: 10:00 a.m. - 12:00 p.m. Wed
  office: TBD
  correspondence_policy: Respond within 24-48 hours
  instructor:
    
# teachingassistant:
#  - name: Filler
#    email: filler@fill.com
#    officehours: W T
#    office: OfficeNumber
#    sections: '301'

classroom: 'Butte Hall 308'
classhours: 2:00 pm - 3:15 pm	TuTh
fontfamily: mathpazo
fontsize: 11pt
header-includes: \linespread{1.05}
  -\usepackage{float}
  -\usepackage{booktabs}
  -\usepackage{fontawesome5}
 
---

```{r setup, include=FALSE, ache=F, message=F, warning=F, results="hide"}

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache=TRUE)
knitr::opts_chunk$set(fig.path='figs/')
knitr::opts_chunk$set(cache.path='_cache/')
knitr::opts_chunk$set(warning=F, message=F)

library(timeDate)
library(tibble)
library(dplyr)
library(knitr)
library(RefManageR)
library(knitcitations)
library(rcrossref)
library(bibtex)
library(kableExtra)
library(fontawesome)

bib <- ReadBib("bib_main.bib")
myopts <- BibOptions(bib.style = "authoryear", style="latex", first.inits=FALSE, max.names = 20)

#This code chunk sets up a table of meeting days for the course.
#You can set days of the week for course meetings (e.g. Monday and Wednesday).
#Semester start and end dates are selected and then university holidays like spring break are specified.

#Days of the week that the course meets. Must be full day name in quotes.
Days <- c("Tuesday", "Thursday")

#Semester start date for classes as YYYY/M/D.
SemesterStart <- as.Date("2022/8/22")

#Semester end date for classes as YYYY/M/D.
SemesterEnd <- as.Date("2022/12/09")

#Fall break start and stop date.
FallBreak <-
  seq.Date(
    from = as.Date("2022/11/21"),
    to = as.Date("2022/11/25"),
    by = "day"
  )

#Spring break start and stop date.
SpringBreak <-
  seq.Date(
    from = as.Date("2023/03/13"),
    to = as.Date("2023/03/17"),
    by = "day"
  )

#Creates a list of days within the semester.
SemesterDays <-
  seq.Date(from = SemesterStart, to = SemesterEnd, by = "day")

#Add day before Thanksgiving.
DayBeforeThnks<-as.Date(holiday(
    year = getRmetricsOptions("currentYear"),
    Holiday = c("USThanksgivingDay")))-1

#Full list of holidays that there are no classes including breaks.
Holidays <-
  c(as.Date(holiday(
    year = getRmetricsOptions("currentYear"),
    Holiday = c("USLaborDay", "USVeteransDay","USThanksgivingDay", "USMLKingsBirthday")
  )), SpringBreak, FallBreak, DayBeforeThnks)
Holidays

#Create a list of semester days excluding holidays.
SemesterDays <- SemesterDays[!SemesterDays %in% Holidays]
SemesterDays
#Make dataframe with all semester days.
ClassDays <- data.frame(index = 1:length(SemesterDays))

#Insert dates.
ClassDays$Date <- SemesterDays

#Insert weekday designation.
ClassDays$Weekday <- weekdays(ClassDays$Date)

#Limit to the class meeting days.
MeetingDays <- ClassDays[ClassDays$Weekday %in% Days, ]

#Create numeric list of weeks.
Week <- cut.Date(MeetingDays$Date, breaks = "week")
levels(Week) <- 1:length(levels(Week))

MeetingDays$Week <- Week
MeetingDays$Class <- 1:nrow(MeetingDays)

#Replace this with c("Lecture topic 1",...,"Lecture topic N") to fill in table.

Lecture_Topic <- 1:nrow(MeetingDays)


MeetingDays <- bind_cols(MeetingDays, Lecture = Lecture_Topic)

#### Grade table ####
Grades <- tribble( ~ Grade,
                   ~ Range, ~Quality,
                   "A",
                   "93 - 100%", "Excellent Work",
                   "A-",
                   "90 - 92%", "Nearly Excellent Work",
                   "B+",
                   "87 - 89%", "Very Good Work", 
                   "B",
                   "83 - 86%", "Good Work",
                   "B-",
                   "80 - 82%", "Mostly Good Work",
                   "C+",
                   "77 - 79%", "Above Average Work",
                   "C",
                   "73 - 76%", "Average Work",
                   "C-",
                   "70 - 72%", "Mostly Average Work",
                   "D+",
                   "67 - 69%", "Below Average Work",
                   "D",
                   "60 - 66%", "Poor Work",
                   "F",
                   "< 60%", "Failing Work")

####Assignment weight table####
Weights <- tribble(~ Item,
                    ~ Weight,
                    "Attendance & Participation",
                    "15 %",
                    "Weekly Perusall Participation & Discussion",
                    "15 %",
                    "Quizzes", 
                    "15 %",
                    "Three (3) Writing Assignments",
                    "25 %", 
                    "Final Paper",
                    "30 %", 
                    "TOTAL", 
                    "100 %"
                  )


```

```{r indigenous_land_statement, child='general_components/indigenous_land_statement.md'}


```

# Course Description

We all construct and use social theories in our everyday lives. Theory is simply a means of understanding and explaining the social world around us. Social theory allows for seeing patterns, forces, and power relations, encouraging us to make sense of all kinds of social phenomena – ranging from everyday interactions between friends to decades of violent colonization. In this course, we will read theoretical texts every week, and then we will spend time understanding how they have been used to understand specific social phenomena. Theory must be relevant to real life “social facts” for it to survive, and we will work toward bridging the abstract concepts in our readings with the world around us. By the end of the class, you will likely find that some theories are your favorites – more relevant to your everyday life and your own sociological interests than others.

The goal of this course is to deepen your understanding of sociological theories that motivate research and inquiry into our society. In this class, we explore the diversity of major theoretical orientations in sociological thought since the 1950s. Throughout the course of the semester, we will compare core concepts and ideas from these theorists on topics such as social interaction, identity, domination, freedom and perhaps most importantly, power. 

This course requires you to read a lot of social theory, which will be abstract and difficult. I assign primary texts, meaning that they were written by the theorist him/herself. The textbook supplements primary texts by elaborating important notions and concepts across the multipe theoretical perspectives we will cover in the course. While we will contextualize the readings by learning about the theorist’s life, it is important that you learn to read with patience and diligence. I am here to help, as are your classmates. If you are struggling to understand course material on your own, that’s okay! No sociologist learns theory on their own. In this class we situate the readings within their historical and biographical contexts and in conversation with other readings. Through lectures, multiple readings of the material on your own, and class discussions, we will – together – arrive at a deeper understanding of our social world and of the history of sociological thought. 

# Learning Objectives

## Course Learning Objectives
- Gain knowledge about some of the primary theoretical perspectives used within sociology in the 20th and 21st centuries.
- Understand how these perspectives have been shaped by the social context in which they arose. 
- Explore how these perspectives have impacted sociological research and knowledge. 
- Evaluate the strengths and weaknesses of each perspective. 
- Apply the perspectives to our real lives and to the world around us. 

## Sociology Program Student Learning Objectives 
- Demonstrate critical thinking through verbal and written communication. 
- Apply, critically interpret, and synthesize sociological theory. 
- Display an understanding of and appreciation for cultural diversity. 
- Identify processes of social control and how they shape our social institutions and lives. 
- Recognize the relationship between personal agency, social responsibility, and social change (sociological imagination). 
- Display knowledge of the impact of social institutions on everyday lives.

## Course Status
This course is a requirement for the sociology major.It has a prerequisite of SOCI 300, Classical Social Theory, though this prerequisite may be waived with permission of the instructor. *Note that if you take SOCI 301 prior to or concurrent with SOCI 300, you will not be able to repeat SOCI 300 for forgiveness.*

## Important Dates
Sept. 2nd - Last day to drop without instructor's approval\
Oct. 24th - Last day to drop and receive financial credit for refund\
Nov. 10th - Last day to drop or withdraw\
See the [2022-2023 Academic Calendar](https://www.csuchico.edu/apss/calendar/aca-cal-2022-23.shtml) for more information.

# Course Readings

## Required Textbooks

```{r new, echo = FALSE, results="asis"} 

bib["dillon2010twp"]

``` 

- We will be using the 3rd edition which looks [this](https://www.abebooks.com/Introduction-Sociological-Theory-Theorists-Concepts-Applicability/31208296728/bd?cm_mmc=ggl-_-US_Shopp_Textbook-_-product_id=COM9781119410911USED-_-keyword=&gclid=Cj0KCQjwuO6WBhDLARIsAIdeyDLJvr2N_LKW1qd-49HuMemlLuCRQT4yR3PKWnmeqMDWBDwy9LNFFRUaAlcyEALw_wcB). Previous editions are not permitted. 

## Additional Required Readings

-  Primary texts and other required readings will be available electronically on the Blackboard Learn course page and on Perusall.

# Structure and Character of a ChicoFlex Course 

-  **Since this is a [*ChicoFlex* Course](https://www.csuchico.edu/tlp/chicoflex/faq.shtml#whatiscoflex), ALL communications for this course will be conducted via Blackboard Learn**. At Chico State, “this class meets at set days/times in-person (requiring social distancing and face coverings) and is paired with another section taught simultaneously online by the same instructor.” This means that this class includes campus students who come to a physical class, online students who show up “live,” and online students who watch the archived lectures. Therefore, it is the student’s responsibility to check Blackboard Learn regularly and to check in with the professor or review the Syllabus re: any administrative questions. *Students are required to email the instructor from Blackboard Learn (this will ensure instructor access to emails).*

-  Also, given the fact that we’re still in a global pandemic, the course will proceed fluidly. I want this class to work for all of us and will remain sensitive to the ongoing needs of students while adhering to public health standards and guidelines. 

## Technological Problems: 

- Occasional problems with technology are a common part of the modern university experience. If you have any technical difficulties, you **should call the university technology folks at 530-898-6000**. After you call them, if they are not able to resolve the issue, please email me with a description of the problem, the name of the person you spoke to in that office, what they and/or you are doing to resolve the problem, and the expected timeline for its resolution. If you are having trouble with Blackboard Learn during a quiz or other assignment, take a screen shot or photo of the computer screen and the error message you receive and email it to me AND contact ITSS at 530-898-6000. If you experience technical difficulties while submitting an assignment, call ITSS at 1-800-898-6000 and send a copy of the assignment to me via Blackboard Learn. If any of these things happen when ITSS is closed, please follow up with them immediately the next business day. You MUST contact ITSS to resolve the issue if you are asking for any kind of leniency or extension. 

```{r covid-19 policy, child='general_components/COVID_policy.md'}

```

```{r attendance_policy, child='general_components/attendance_policy.md'}

```

# Determination of Final Grade

Table \ref{tab:grade_scale} displays the grading scale that is used to determine a letter grade.

\renewcommand{\arraystretch}{1.5}

```{r Grades_Table, echo=FALSE, results='asis'}

kable(Grades,
      align = c("l", "c", "l"),format="latex",  
      label="grade_scale", caption="Grading Scale") %>%
  kable_styling(font_size=10, latex_options = "hold_position", full_width = F) %>%
  row_spec(0, bold=T) 

```

Table \ref{tab:weight_table} displays how your final grade will be weighed according to the following components:

\renewcommand{\arraystretch}{1.5}

```{r Weights_Table, echo=FALSE, results='asis'}
kable(Weights,
      align = c("l", "c"), format="latex", booktabs=T, 
      col.names = c("Item", "% of Final Grade"), 
      label="weight_table", caption="Course Requirements and Grading Policy") %>%
  kable_styling(font_size=10, latex_options = c("hold_position"), full_width = F) %>%
  row_spec(0, bold=T) %>%
  row_spec(6, bold=T, hline_after = T)

```

**Note regarding class workload:** This is a three (3) credit hour class. You should expect to spend two hours outside of class for every one hour in class. This time outside of class will be spent on reading, assignments, and studying. This means you should plan on devoting six hours of outside time per week to this course.     

\newpage

## Attendance and Class Participation (15% of Final Grade)

The format of this course is an interactive, “live” hybrid lecture and discussion with the objective of collaborative learning and analysis. Participation in class discussion is necessary for your development as a critical scholar and for your understanding of the course material. This is a **required** course with difficult reading material and, therefore, it is crucial to establish an informed and critical discourse with each other over the material. Participation includes contributions to class discussions either in class or via class assignments. Participation also includes actively listening, as well as sharing your ideas, criticisms, and frustrations with course material. To ensure active participation, students must come to class having read and taken notes on all material. Furthermore, you are expected to contribute to discussions either in class or via class assignments. Grading of all work is done with the expectation that attendance and participation will be rewarded in the final grade. Also, see “COVID Directions” (above) if you are symptomatic and an in-class student. 

In addition to completing all of the assigned reading before each designated day of the week (see reading schedule below and make sure you attend class for the ongoing reading deadlines), you must critically reflect on what is interesting/troubling/useful about what you have read. You are expected to do this work on your own. Be prepared to offer your questions, insights, and critique either via communication with me, writing assignments and/or in conversation with other students. 

*These are questions you should consider as you complete each reading:* What are the authors’ main objectives/research questions?  What methods, if any, did the author use to explore this question? What are the author’s main conclusions?  How do the readings build upon or challenge other works we have read thus far? Answering these questions on your own will better prepare you for quizzes, writing assignments, and the final project.

**REMEMBER! Attendance is mandatory in all sociology classes (see [Attendance Policy section](#attendance) above). It is also crucial to doing well in this class. In the context of this class, attendance means COMPLETING ALL OF THE ASSIGNMENTS, QUIZZES, INDIVIDUAL WORK, etc.** *I usually have a very strict attendance policy.* 

```{r perusall_participation, child='general_components/perusall_participation.md'}

```

## Quizzes (15% of Final Grade)
Throughout the course, I will ask students to synthesize, analyze, and/or apply contemporary social theories and readings from the previous day(s) or week(s) via a fairly short, intense quiz (typically, 3-10 multiple-choice and/or short answer questions). The quiz closes after the posted due date. In order to avoid missing a quiz and any announcements I have, make sure you check Blackboard Learn every single day of the week. The quiz closes after the posted due date. In order to avoid missing a quiz and any announcements I have, make sure you check Blackboard Learn every single day of the week. *No quiz will be assigned the week a writing assignment is due.*

## Three (3) Writing Assignments (25% of Final Grade) {#writing_assignments}
Students will complete at least 3 small writing assignments throughout the course. These assignments will assess knowledge of the course material, critical thinking skills, and writing skills. Guidelines for the papers will be given out at least two weeks in advance. Papers will have a word limit, approx. 750 words (roughly 3 double-spaced pages), typed, 12-point font, 1-inch margins, Times New Roman (11-point Arial font is also appropriate). Proper grammar and APA citation of sources is expected. **No other format will be accepted.** Late papers will be deducted 20% of its overall grade each day that it is overdue. 

## Final Paper (30% of Final Grade)
Building upon the ideas you developed in the writing assignments and other assignments, you will write a **final 1,000 word (roughly 4 double-spaced pages) paper for this class.** In this paper, you will apply, expand, or challenge theories we covered in class. In this paper, you will apply, expand, or challenge theory. If you apply theory, you will use one of the main theoretical frameworks we covered in the course to sociologically analyze a cultural artifact (examples: documentary film(s), popular film(s), popular music, magazines, novels, etc.; speak with me about the appropriate cultural artifact). If you expand theory, you will make an argument for the expansion of any theory we have covered in the course, thus making that theory better, more contemporary, and/or more inclusive. If you challenge theory, you will accurately describe the theory you are challenging, make an argument for how and why you are challenging the theory, and perhaps offer a new theory that might replace the theory you are challenging. Before you begin your paper, speak with me about your main ideas and outline for the paper. I will post a detailed rubric and example of an excellent Final Paper on Blackboard about a month before the due date. 

### Tips and tricks for good writing

Use a citation management software to organize your papers and create bibiliographies. My personal preference is [Zotero](https://www.zotero.org/) because it is free, open source, and works across multiple operating systems. For information about other citation management software that is available to CSU Chico students, visit the Meriam Library ["Sample Papers and Citation Tools" page](https://libguides.csuchico.edu/c.php?g=432300&p=2948649). 

Write and then revise. Ask for feedback from peers or wait until you have some distance from your writing and then revise.

Prompt yourself with questions that have short, concrete answers.

```{r late_work-course_eval, child='general_components/late_work-course_eval.md'}

```

```{r contacting_professor, child='general_components/contacting_professor.md'}

```

# Creating a Safe and Inclusive Learning Environment 

```{r mandatory_reporting, child='general_components/mandatory_reporting.md'}

```

```{r Diversity Statements, child='general_components/diversity_statements.md'}

```

```{r Mental Health, child='general_components/mental_health.md'}

```

```{r other_course_policies, child='general_components/other_course_policies.md'}

```

# University Policies and Campus Resources

```{r Academic Integrity, child='general_components/academic_integrity.md'}

```

```{r Student Services, child='general_components/student_services.md'}

```

```{r Disability Services, child='general_components/disability_services.md'}

```

```{r Food Insecurity, child='general_components/food_insecurity.md'}

```

# Final thoughts

This document is a roadmap for our semester. We learn about the Earth together and our individual experiences shape how we interpret and value data. Like all your classes, you will get out what you put into this course. Asking for help from one another and your instructors is important, don't be afraid to ask a question about something you don't know or if you want to check your knowledge about something you think you know.

__If this document is updated, a copy will be supplied to you via Black Board and changes will be announced in class.__

\newpage 

\renewcommand{\arraystretch}{1.25}

```{r Schedule, echo=FALSE}
kable(MeetingDays[,c("Date",
                     "Class",
                     "Week",
                     "Lecture")
                     ],
  caption = "Course Schedule.",
  align = c("l",
            "c",
            "c",
            "l")
)
```

